---
title: "CA costs - Experiment 4"
author: "Ivan Grahek"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## About the code

Experiment: Control adjustment costs Experiment 4 (Probability experiment)
Code written by: Ivan Grahek (2022)
Description: Code for the analysis of behavioral data for Experiment 4 of the Control adjustment costs project.  

\newpage

# Load the libraries 


```{r, message=FALSE}
# clear the environment
rm(list=ls()) 

# set seed
set.seed(42) 

#load packages and install them if they're not installed. the pacman package will 
#automatically check for the requested packages and download & install them if they are not on the computer.
if (!require("pacman")) install.packages("pacman")
pacman::p_load(brms,here,broom,knitr,tidyverse,plyr,cowplot,emmeans,tidybayes,viridis,MASS)

# Define the summary posterior function
summarize_posterior <- function(model,variable) {
   post = posterior_samples(model, "^b")
   ggplot(post,aes_string(x=paste0("`",variable,"`"))) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(variable,"p<0 = ",length(subset(post[[variable]],post[[variable]]<0))/length(post[[variable]]))) +
     theme_classic() 

}

# Define the difference summary posterior function
summarize_difference_posterior <- function(V1,V2,effect) {
   post = as.data.frame(V1-V2)
   ggplot(data=post,aes(x=`V1 - V2`)) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(effect,"p<0 = ",length(post[post<0])/length(post$`V1 - V2`))) +
     theme_classic() 

}

# Define calculate the posterior probabilities function
posterior_probabilities <- function(model) {
   parameter_names = rownames(summary(model)[["fixed"]])
   post_prob = rep(0,length(parameter_names))
   for (i in 1:length(parameter_names)){
     t = hypothesis(model,paste0(parameter_names[i],"<0"))
     post_prob[i] = t$hypothesis$Post.Prob
   }
  return(post_prob)
}

```




# Main analyses

## Reaction times

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.RT.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
pp_check(model,type="dens_overlay_grouped",group="Congruency")
pp_check(model,type="dens_overlay_grouped",group="intervalType")
pp_check(model,type="dens_overlay_grouped",group="blockType")

```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL

# add a row name column
# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```


### Plotting the  model

```{r, warning=FALSE, message=FALSE}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                            "b_blockTypeLinear",
                                            "b_blockTypeQuadratic",
                                            "b_blockTypeCubical"))
# Remove the non-necessary variables
posterior = posterior[,1:4]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Get the main effects of block type
BlockType = cbind(c(1,1,1,1),contr.poly(4))
MainEffects =  as.data.frame(t(BlockType %*% t(posterior)))
colnames(MainEffects) = c("Main_2intervals","Main_4intervals","Main_8intervals","Main_Fixed")

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_intervalTypeSpeed_min_Accuracy",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeLinear",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeQuadratic",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeCubical"))

# Remove the non-necessary variables
posterior = posterior[,1:4]

# Get the interactions
BlockType = cbind(c(1,1,1,1),contr.poly(4))
Interactions =  as.data.frame(t(BlockType %*% t(posterior)))
colnames(Interactions) = c("Interactions_2intervals","Interactions_4intervals","Interactions_8intervals","Interactions_Fixed")

# Calculate per condition
results = as.data.frame(matrix(1,length(MainEffects$Main_2intervals)))

results$Speed_2intervals = MainEffects$Main_2intervals + Interactions$Interactions_2intervals 
results$Accuracy_2intervals = MainEffects$Main_2intervals - Interactions$Interactions_2intervals 

results$Speed_4intervals = MainEffects$Main_4intervals + Interactions$Interactions_4intervals 
results$Accuracy_4intervals = MainEffects$Main_4intervals - Interactions$Interactions_4intervals

results$Speed_8intervals = MainEffects$Main_8intervals + Interactions$Interactions_8intervals 
results$Accuracy_8intervals = MainEffects$Main_8intervals - Interactions$Interactions_8intervals

results$Speed_Fixed = MainEffects$Main_Fixed + Interactions$Interactions_Fixed 
results$Accuracy_Fixed = MainEffects$Main_Fixed - Interactions$Interactions_Fixed

# Remove the first row
results = results[,-1]


results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Block Type'),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Accuracy","Speed"))
results$`Block Type` = factor(results$`Block Type`, levels = c("Fixed","8intervals","4intervals","2intervals"))


# Plot
p = ggplot(results,aes(x=`Block Type`,y=Estimate,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) +
  guides(color = guide_legend(override.aes=list(shape = 20)))+
    ylab("Reaction times (ms)")+
  xlab("Performance goal")+
  scale_y_continuous(limits = c(600,850))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+

  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(linewidth=0.5),
        axis.line.y.left=element_line(linewidth=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        legend.background = element_rect(fill = "transparent", color = NA))  
p
Fig5.RT = p

```



## Accuracy

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.Acc.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
pp_check(model,type="dens_overlay_grouped",group="Congruency")
pp_check(model,type="dens_overlay_grouped",group="intervalType")
pp_check(model,type="dens_overlay_grouped",group="blockType")
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL


# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```



### Plotting the  model

```{r, warning=FALSE, message=FALSE}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                            "b_blockTypeLinear",
                                            "b_blockTypeQuadratic",
                                            "b_blockTypeCubical"))
# Remove the non-necessary variables
posterior = posterior[,1:4]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Get the main effects of block type
BlockType = cbind(c(1,1,1,1),contr.poly(4))
MainEffects =  as.data.frame(t(BlockType %*% t(posterior)))
colnames(MainEffects) = c("Main_2intervals","Main_4intervals","Main_8intervals","Main_Fixed")

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_intervalTypeSpeed_min_Accuracy",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeLinear",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeQuadratic",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeCubical"))

# Remove the non-necessary variables
posterior = posterior[,1:4]

# Get the interactions
BlockType = cbind(c(1,1,1,1),contr.poly(4))
Interactions =  as.data.frame(t(BlockType %*% t(posterior)))
colnames(Interactions) = c("Interactions_2intervals","Interactions_4intervals","Interactions_8intervals","Interactions_Fixed")

# Calculate per condition
results = as.data.frame(matrix(1,length(MainEffects$Main_2intervals)))

results$Speed_2intervals = MainEffects$Main_2intervals + Interactions$Interactions_2intervals 
results$Accuracy_2intervals = MainEffects$Main_2intervals - Interactions$Interactions_2intervals 

results$Speed_4intervals = MainEffects$Main_4intervals + Interactions$Interactions_4intervals 
results$Accuracy_4intervals = MainEffects$Main_4intervals - Interactions$Interactions_4intervals

results$Speed_8intervals = MainEffects$Main_8intervals + Interactions$Interactions_8intervals 
results$Accuracy_8intervals = MainEffects$Main_8intervals - Interactions$Interactions_8intervals

results$Speed_Fixed = MainEffects$Main_Fixed + Interactions$Interactions_Fixed 
results$Accuracy_Fixed = MainEffects$Main_Fixed - Interactions$Interactions_Fixed

# Remove the first row
results = results[,-1]


results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Block Type'),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Accuracy","Speed"))
results$`Block Type` = factor(results$`Block Type`, levels = c("Fixed","8intervals","4intervals","2intervals"))

# Turn logits into probabilities
results$Estimate = exp(results$Estimate)
results$Estimate = results$Estimate / (1 + results$Estimate)

results$Q2.5 = exp(results$Q2.5)
results$Q2.5 = results$Q2.5 / (1 + results$Q2.5)

results$Q97.5 = exp(results$Q97.5)
results$Q97.5 = results$Q97.5 / (1 + results$Q97.5)

# Plot
p = ggplot(results,aes(x=`Block Type`,y=Estimate,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) +
  guides(color = guide_legend(override.aes=list(shape = 20)))+
  ylab("Accuracy")+
  xlab("Performance goal")+
  scale_y_continuous(limits = c(0.58,1))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+

  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(linewidth=0.5),
        axis.line.y.left=element_line(linewidth=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        legend.background = element_rect(fill = "transparent", color = NA))  



p


Fig5.Acc = p

```




# Save the figures


```{r, warning=FALSE, message=FALSE}

# pdf(file="../../../Manuscript/figures/Figure_5_behavior.pdf",height=4,width=20)
# 
# p = cowplot::plot_grid(Fig5.RT,
#                        Fig5.Acc,
#                        nrow = 1)
# p
# dev.off()


pdf(file="../../../Manuscript/figures/Figure_5_behavior.pdf",height=6,width=20)

p = cowplot::plot_grid(Fig5.RT,
                       Fig5.Acc,
                       nrow = 1)
p
dev.off()

```

