---
title: "Experiment 1 analysis"
author: "Ivan Grahek"
date: "01/03/2022"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




# Load the data and the packages

```{r,warning=FALSE,echo=FALSE,message=FALSE}
# clear the environment
rm(list=ls()) 
#load packages and install them if they're not installed
if (!require("pacman")) install.packages("pacman")
pacman::p_load(plyr,tidyverse, lme4,MASS,sjPlot,coefplot,cowplot,psych,rmarkdown,knitr,kable,cowplot)

# set seed
set.seed(42) 

df.trial = read_csv("../../Data/ProcessedData/CleanDataSpeedAccuracyV3_nSubs_44.csv")

```

# Descriptives and design checks

```{r , results='asis'}

# Interval types
summary_table = ddply(df.trial,.(SubID,blockType,intervalType),plyr::summarize,
                                       MeanRT=mean(rt,na.rm=TRUE), # mean RT per condition
                                       MeanAcc=mean(hit,na.rm=TRUE), 
                                       Ntrials=length(hit))
print(kable(summary_table, align="l", caption="Interval types"))


# summary_table = ddply(df.trial,.(blockType,intervalType,type,trialNum),plyr::summarize,
#                                        Ntrials=length(hit))%>%
#   filter(trialNum<6)
# 
# plot = ggplot(data=summary_table,
#                aes(x=trialNum,y=Ntrials,group=type))+
#                geom_line(aes(linetype=type),size=1)+ 
#                geom_point(size=2)+
#                  facet_grid(.~blockType) + 
# 
#   scale_x_continuous(breaks = 1:10)+
#     theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
#         axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
#         text = element_text(size=20),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))



# # Accuracy per subject
# summary_table = ddply(df.trial,.(SubID),plyr::summarize,
#                                        MeanRT=mean(rt,na.rm=TRUE), # mean RT per condition
#                                        MeanAcc=mean(hit,na.rm=TRUE), 
#                                        Ntrials=length(hit))
# print(kable(summary_table, align="l", caption="Accuracy"))


df.errors<-df.trial%>%
  filter(hit==0)%>%
  dplyr::select(SubID,ErrorType,rt,intervalType)

 df.errorTypesSummary<-df.errors %>%
    dplyr:: group_by(SubID,ErrorType,intervalType) %>%
    dplyr::  summarise(count=n(),
                       avgRT=mean(rt))
 
 
  # df.allErrorsSummary<-df.errors %>%
  #   group_by(SubID,intervalType) %>%
  #   count=count(type,.drop = FALSE)
  

 
 
#  # For each subject
# for (subject in 1:length(unique(df.errorTypesSummary$SubID))) {
# 
#   #Plotting
#   plot_data = subset(df.errorTypesSummary,df.errorTypesSummary$SubID == unique(df.errorTypesSummary$SubID)[subject])
#   
#   plot = ggplot(plot_data, aes(x=intervalType,y=count, fill=ErrorType)) + 
#   geom_bar(stat="identity", color="black", position=position_dodge(.9))+
#   # geom_point(size=2)+
#   # scale_y_continuous(limits=c(500,1500)) + 
#   ggtitle(paste0('Error types - Subject ',unique(df.errorTypesSummary$SubID)[subject])) +
#   theme_classic(base_size = 10) 
# 
#   print(plot)
#     # print(Acc)
# 
# }

```



# Permutation 
```{r}

# 1 - do the permutation on df.interval
Permuted = subset(df.trial, df.trial$blockType=="Fixed")
df.interval <- Permuted %>% 
  group_by(SubID,Version,blockNum,intervalNum,intervalLength,intervalType) %>% 
  dplyr::summarise(trialsPerInterval = n())

df.interval <- df.interval %>%
  group_by(SubID,blockNum) %>%
  mutate(random = row_number()) %>%
  mutate(random = random[sample(row_number())])

# Permute 10%
df.interval$intervalTypePermute10 = ifelse(df.interval$intervalType=="Speed" & df.interval$random<4,"Accuracy",as.character(df.interval$intervalType))
df.interval$intervalTypePermute10 = ifelse(df.interval$intervalType=="Accuracy" & df.interval$random<4,"Speed",as.character(df.interval$intervalTypePermute10))

# Permute 20%
df.interval$intervalTypePermute20 = ifelse(df.interval$intervalType=="Speed" & df.interval$random<7,"Accuracy",as.character(df.interval$intervalType))
df.interval$intervalTypePermute20 = ifelse(df.interval$intervalType=="Accuracy" & df.interval$random<7,"Speed",as.character(df.interval$intervalTypePermute20))

# Permute 30%
df.interval$intervalTypePermute30 = ifelse(df.interval$intervalType=="Speed" & df.interval$random<10,"Accuracy",as.character(df.interval$intervalType))
df.interval$intervalTypePermute30 = ifelse(df.interval$intervalType=="Accuracy" & df.interval$random<10,"Speed",as.character(df.interval$intervalTypePermute30))


# 2 - inner join df.interval and df.trial by interval number
df.trial.permuted.mixed = plyr::join(subset(df.trial, df.trial$blockType=="Fixed"),df.interval, by = c("SubID", "blockNum", "intervalNum"),type="full")
df.trial.permuted.mixed$blockType = "Varying"

# add the pure fixed blocks again

df.trial.permuted.fixed = df.trial.permuted.mixed
df.trial.permuted.fixed$intervalTypePermute10 = as.character(df.trial.permuted.fixed$intervalType)
df.trial.permuted.fixed$intervalTypePermute20 = as.character(df.trial.permuted.fixed$intervalType)
df.trial.permuted.fixed$intervalTypePermute30 = as.character(df.trial.permuted.fixed$intervalType)
df.trial.permuted.fixed$blockType = "Fixed"

df.trial.permuted = rbind(df.trial.permuted.fixed,df.trial.permuted.mixed)



# ddply(df.trial.permuted,.(blockType,intervalTypePermute20),plyr::summarize,
#                                        MeanRT=mean(rt,na.rm=TRUE), # mean RT per condition
#                                        MeanAcc=mean(hit,na.rm=TRUE), 
#                                        Ntrials=length(hit))
# 
# View(cbind(df.trial.permuted.fixed$SubID,df.trial.permuted.fixed$hit,df.trial.permuted.fixed$blockNum,df.trial.permuted.fixed$intervalNum,df.trial.permuted.fixed$intervalType,df.trial.permuted.fixed$intervalTypePermute10))
# 
# View(cbind(df.trial.permuted.mixed$SubID,df.trial.permuted.mixed$hit,df.trial.permuted.mixed$blockNum,df.trial.permuted.fixed$intervalNum,df.trial.permuted.mixed$intervalType,df.trial.permuted.mixed$intervalTypePermute10))
# 

```



# Re-scale the data

```{r }

# # # take out the random errors
# df.trial = df.trial %>%
#   filter(ErrorType != "random")

df.trial.permuted$blockType = as.factor(df.trial.permuted$blockType)

# Center the continuous variables 
df.trial$scaledIntervalLength = scale(df.trial$scaledIntervalLength, scale= FALSE, center = TRUE)
df.trial$scaledIntervalSessionNum = scale(df.trial$scaledIntervalSessionNum, scale= FALSE, center = TRUE)

# Contrast code the categorical variables
df.trial$Congruency = ordered(df.trial$type, levels = c("congruent", "incongruent"))
contrasts(df.trial$Congruency) = contr.sdif(2)
colnames(attr(df.trial$Congruency, "contrasts")) =  c("inc_min_con")

# Contrast code the categorical variables
df.trial.permuted$Congruency = ordered(df.trial.permuted$type, levels = c("congruent", "incongruent"))
contrasts(df.trial.permuted$Congruency) = contr.sdif(2)
colnames(attr(df.trial.permuted$Congruency, "contrasts")) =  c("inc_min_con")

df.trial$intervalType = ordered(df.trial$intervalType, levels = c("Speed","Accuracy"))
contrasts(df.trial$intervalType) = contr.sdif(2)
colnames(attr(df.trial$intervalType, "contrasts")) =  c("Speed_min_Accuracy")


df.trial.permuted$intervalType = ordered(df.trial.permuted$intervalType, levels = c("Speed","Accuracy"))
contrasts(df.trial.permuted$intervalType) = contr.sdif(2)
colnames(attr(df.trial.permuted$intervalType, "contrasts")) =  c("Speed_min_Accuracy")

df.trial.permuted$intervalTypePermute10 = ordered(df.trial.permuted$intervalTypePermute10, levels = c("Speed","Accuracy"))
contrasts(df.trial.permuted$intervalTypePermute10) = contr.sdif(2)
colnames(attr(df.trial.permuted$intervalTypePermute10, "contrasts")) =  c("Speed_min_Accuracy")

df.trial.permuted$intervalTypePermute20 = ordered(df.trial.permuted$intervalTypePermute20, levels = c("Speed","Accuracy"))
contrasts(df.trial.permuted$intervalTypePermute20) = contr.sdif(2)
colnames(attr(df.trial.permuted$intervalTypePermute20, "contrasts")) =  c("Speed_min_Accuracy")

df.trial.permuted$intervalTypePermute30 = ordered(df.trial.permuted$intervalTypePermute30, levels = c("Speed","Accuracy"))
contrasts(df.trial.permuted$intervalTypePermute30) = contr.sdif(2)
colnames(attr(df.trial.permuted$intervalTypePermute30, "contrasts")) =  c("Speed_min_Accuracy")

df.trial$Switch = ordered(df.trial$Switch, levels = c("Switch","Repeat"))
contrasts(df.trial$Switch) = contr.sdif(2)
colnames(attr(df.trial$Switch, "contrasts")) =  c("Switch_min_Repeat")

df.trial$intervalNumHalf = ifelse(df.trial$intervalNum>15,"Second","First")
df.trial$intervalNumHalf = ordered(df.trial$intervalNumHalf, levels = c("Second","First"))
contrasts(df.trial$intervalNumHalf) = contr.sdif(2)
colnames(attr(df.trial$intervalNumHalf, "contrasts")) =  c("Second_min_First")



```

# Original dataset
## Task Data Analysis 

### Accuracy 

#### All errors 
```{r}

# Specific interaction
model.acc = glmer(hit ~ type + intervalType/(blockType) + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),
                data = df.trial, family = binomial(link="logit"))

tab_model(model.acc,title = "Accuracy - Trial Based")

model.acc = glmer(hit ~ type + intervalType*blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),
                data = df.trial, family = binomial(link="logit"))


p = plot_model(model.acc,type = "pred", terms = c("intervalType","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Block type"

p = p + 
  ggtitle("Accuracy")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc = p

Acc

```




### Response Time 

#### Correct trials

```{r}



# Specific interaction
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalType/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = df.trial, REML = F)

tab_model(model.accrt.,title = "RT - Trial Based")

# Plot
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalType * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = df.trial, REML = F)


p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)


p$labels$colour = "Block type"

p = p + 
  ggtitle("Reaction times")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT = p

RT

```

#### Save

```{r, message=FALSE}
cowplot::plot_grid(RT,Acc, ncol = 2)

ggsave("Exp1_Behavior.tiff", units="in", width=12, height=4, dpi=500, compression = 'lzw')

```








<!-- ### Incorrect trials - all errors -->

<!-- ```{r} -->
<!-- # Specific interaction -->
<!-- model.accrt. = lmer(log10_ErrRT ~ Congruency + intervalType/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = df.trial, REML = F) -->

<!-- tab_model(model.accrt.,title = "RT - Trial Based") -->

<!-- # Plot -->
<!-- model.accrt. = lmer(log10_ErrRT ~ Congruency + intervalType * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType+ blockType|uniqueid),data = df.trial, REML = F) -->

<!-- p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","blockType")) -->
<!-- p +  -->
<!--   ggtitle("All errors")+  -->
<!--   ylab("logRT")+ -->
<!--   theme(axis.line = element_line(colour = "black"), -->
<!--         axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)), -->
<!--         text = element_text(size=20), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_blank(), -->
<!--         panel.background = element_blank(), -->
<!--         axis.title.x=element_blank(), -->
<!--         plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))  -->

<!-- # p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","Congruency")) -->
<!-- # p + theme_classic() -->



<!-- ``` -->






<!-- ### Incorrect trials - automatic errors -->

<!-- ```{r} -->
<!-- # Specific interaction -->
<!-- model.accrt. = lmer(log10_ErrRT ~  intervalType/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = subset(df.trial,df.trial$ErrorType!="random"), REML = F) -->

<!-- tab_model(model.accrt.,title = "RT - Trial Based") -->

<!-- # Plot -->
<!-- model.accrt. = lmer(log10_ErrRT ~  intervalType * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType+ blockType|uniqueid),data = subset(df.trial,df.trial$ErrorType!="random"), REML = F) -->


<!-- p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","blockType")) -->
<!-- p +  -->
<!--   ggtitle("Automatic errors")+  -->
<!--   ylab("logRT")+ -->
<!--   theme(axis.line = element_line(colour = "black"), -->
<!--         axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)), -->
<!--         text = element_text(size=20), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_blank(), -->
<!--         panel.background = element_blank(), -->
<!--         axis.title.x=element_blank(), -->
<!--         plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))  -->

<!-- # p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","Congruency")) -->
<!-- # p + theme_classic() -->



<!-- ``` -->






<!-- ### Incorrect trials - random errors -->

<!-- ```{r} -->
<!-- # Specific interaction -->
<!-- model.accrt. = lmer(log10_ErrRT ~ Congruency + intervalType/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = subset(df.trial,df.trial$ErrorType!="automatic"), REML = F) -->

<!-- tab_model(model.accrt.,title = "RT - Trial Based") -->

<!-- # Plot -->
<!-- model.accrt. = lmer(log10_ErrRT ~ Congruency + intervalType * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType+ blockType|uniqueid),data = subset(df.trial,df.trial$ErrorType!="automatic"), REML = F) -->


<!-- p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","blockType")) -->
<!-- p +  -->
<!--   ggtitle("Random errors")+  -->
<!--   ylab("logRT")+ -->
<!--   theme(axis.line = element_line(colour = "black"), -->
<!--         axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)), -->
<!--         text = element_text(size=20), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_blank(), -->
<!--         panel.background = element_blank(), -->
<!--         axis.title.x=element_blank(), -->
<!--         plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))  -->

<!-- # p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","Congruency")) -->
<!-- # p + theme_classic() -->



<!-- ``` -->








## Switch repeat analysis

### Accuracy 

#### All errors 
```{r}

# Specific interaction
model.acc = glmer(hit ~ type + intervalType/Switch + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + Switch|uniqueid),
                data = subset(df.trial,df.trial$blockType=="Mixed"), family = binomial(link="logit"))

tab_model(model.acc,title = "Accuracy - Trial Based")

model.acc = glmer(hit ~ type + intervalType*Switch + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + Switch|uniqueid),
                data = subset(df.trial,df.trial$blockType=="Mixed"), family = binomial(link="logit"))


p = plot_model(model.acc,type = "pred", terms = c("intervalType","Switch"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Switch"

p = p + 
  ggtitle("Accuracy - Mixed blocks")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc_Switch = p

Acc_Switch





# Repeat trials from the fixed blocks

model.acc = glmer(hit ~ type + intervalType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType|uniqueid),
                data = subset(df.trial,df.trial$blockType=="Fixed"), family = binomial(link="logit"))

p = plot_model(model.acc,type = "pred", terms = c("intervalType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Switch"

p = p + 
  ggtitle("Accuracy - Fixed blocks")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc_Repeat_Fixed = p

Acc_Repeat_Fixed

```


### Response Time 

#### Correct trials

```{r}
# Specific interaction
model.accrt. = lmer(log10_AccRT ~ type + intervalType/Switch  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType +Switch|uniqueid),data = subset(df.trial,df.trial$blockType=="Mixed"), REML = F)

tab_model(model.accrt.,title = "RT - Trial Based")

# Plot
model.accrt. = lmer(log10_AccRT ~ type + intervalType  * Switch + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType +Switch|uniqueid),data = subset(df.trial,df.trial$blockType=="Mixed"), REML = F)

p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","Switch"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Switch"

p = p + 
  ggtitle("Reaction times - Mixed blocks")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT_Switch = p

RT_Switch

# Repeat trials from the fixed blocks
# Plot
model.accrt. = lmer(log10_AccRT ~ type + intervalType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType|uniqueid),data = subset(df.trial,df.trial$blockType=="Fixed"), REML = F)

p = plot_model(model.accrt.,type = "pred", terms = c("intervalType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Switch"

p = p + 
  ggtitle("Reaction times - Fixed blocks")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT_Repeat_Fixed = p

RT_Repeat_Fixed

```




#### Save

```{r, message=FALSE}
cowplot::plot_grid(RT_Switch,RT_Repeat_Fixed,Acc_Switch,Acc_Repeat_Fixed, ncol = 2)

ggsave("Exp1_V3_SwitchRpeat.tiff", units="in", width=12, height=8, dpi=500, compression = 'lzw')

```












# 0% Permuted dataset


## Task Data Analysis 

### Accuracy 

#### All errors 
```{r}

# Specific interaction
model.acc = glmer(hit ~ type + intervalType/(blockType) + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))

tab_model(model.acc,title = "Accuracy - Trial Based")

model.acc = glmer(hit ~ type + intervalType*blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))


p = plot_model(model.acc,type = "pred", terms = c("intervalType","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Block type"

p = p + 
  ggtitle("Accuracy")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc = p

Acc
```


### Response Time 

#### Correct trials

```{r}


# Specific interaction
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalType/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = df.trial.permuted, REML = F)


tab_model(model.accrt.,title = "RT - Trial Based")

# Plot
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalType * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalType + blockType|uniqueid),data = df.trial.permuted, REML = F)


p = plot_model(model.accrt.,type = "pred", terms = c("intervalType","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)


p$labels$colour = "Block type"

p = p + 
  ggtitle("Reaction times")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT = p

RT

```

#### Save

```{r, message=FALSE}
# cowplot::plot_grid(RT,Acc, ncol = 2)
# 
# ggsave("Exp1_Behavior.tiff", units="in", width=12, height=4, dpi=500, compression = 'lzw')

```







# 10% Permuted dataset


## Task Data Analysis 

### Accuracy 

#### All errors 
```{r}

# Specific interaction
model.acc = glmer(hit ~ type + intervalTypePermute10/(blockType) + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute10 + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))

tab_model(model.acc,title = "Accuracy - Trial Based")

model.acc = glmer(hit ~ type + intervalTypePermute10*blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute10 + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))


p = plot_model(model.acc,type = "pred", terms = c("intervalTypePermute10","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Block type"

p = p + 
  ggtitle("Accuracy")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc = p

Acc
```


### Response Time 

#### Correct trials

```{r}
# Specific interaction
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalTypePermute10/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute10 + blockType|uniqueid),data = df.trial.permuted, REML = F)


tab_model(model.accrt.,title = "RT - Trial Based")

# Plot
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalTypePermute10 * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute10 + blockType|uniqueid),data = df.trial.permuted, REML = F)


p = plot_model(model.accrt.,type = "pred", terms = c("intervalTypePermute10","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)


p$labels$colour = "Block type"

p = p + 
  ggtitle("Reaction times")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT = p

RT

```

#### Save

```{r, message=FALSE}
# cowplot::plot_grid(RT,Acc, ncol = 2)
# 
# ggsave("Exp1_Behavior.tiff", units="in", width=12, height=4, dpi=500, compression = 'lzw')

```







# 20% Permuted dataset


## Task Data Analysis 

### Accuracy 

#### All errors 
```{r}

# Specific interaction
model.acc = glmer(hit ~ type + intervalTypePermute20/(blockType) + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute20 + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))

tab_model(model.acc,title = "Accuracy - Trial Based")

model.acc = glmer(hit ~ type + intervalTypePermute20*blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute20 + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))


p = plot_model(model.acc,type = "pred", terms = c("intervalTypePermute20","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Block type"

p = p + 
  ggtitle("Accuracy")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc = p

Acc
```


### Response Time 

#### Correct trials

```{r}
# Specific interaction
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalTypePermute20/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute20 + blockType|uniqueid),data = df.trial.permuted, REML = F)


tab_model(model.accrt.,title = "RT - Trial Based")

# Plot
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalTypePermute20 * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute20 + blockType|uniqueid),data = df.trial.permuted, REML = F)


p = plot_model(model.accrt.,type = "pred", terms = c("intervalTypePermute20","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)


p$labels$colour = "Block type"

p = p + 
  ggtitle("Reaction times")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT = p

RT

```

#### Save

```{r, message=FALSE}
# cowplot::plot_grid(RT,Acc, ncol = 2)
# 
# ggsave("Exp1_Behavior.tiff", units="in", width=12, height=4, dpi=500, compression = 'lzw')

```









# 20% Permuted dataset


## Task Data Analysis 

### Accuracy 

#### All errors 
```{r}

# Specific interaction
model.acc = glmer(hit ~ type + intervalTypePermute30/(blockType) + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute30 + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))

tab_model(model.acc,title = "Accuracy - Trial Based")

model.acc = glmer(hit ~ type + intervalTypePermute30*blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute30 + blockType|uniqueid),
                data = df.trial.permuted, family = binomial(link="logit"))


p = plot_model(model.acc,type = "pred", terms = c("intervalTypePermute30","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)

p$labels$colour = "Block type"

p = p + 
  ggtitle("Accuracy")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
    scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))

Acc = p

Acc
```


### Response Time 

#### Correct trials

```{r}
# Specific interaction
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalTypePermute30/blockType  + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute30 + blockType|uniqueid),data = df.trial.permuted, REML = F)


tab_model(model.accrt.,title = "RT - Trial Based")

# Plot
model.accrt. = lmer(log10_AccRT ~ Congruency + intervalTypePermute30 * blockType + scaledIntervalSessionNum + scaledIntervalLength + (1 + intervalTypePermute30 + blockType|uniqueid),data = df.trial.permuted, REML = F)


p = plot_model(model.accrt.,type = "pred", terms = c("intervalTypePermute30","blockType"),colors = c(rgb(0.1, 0.1, 0.1),rgb(0.5, 0.5, 0.5)),dot.size = 2.5, line.size = 1.5,dodge = .3)


p$labels$colour = "Block type"

p = p + 
  ggtitle("Reaction times")+ 
  ylab("log RT")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed",
     "Accuracy"), expand=c(0.3, 0.3))+

  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        # axis.ticks.length.x.left = unit(.25,"cm"),
        # axis.text.x=element_blank(),
        # axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"))


RT = p

RT

```

#### Save

```{r, message=FALSE}
# cowplot::plot_grid(RT,Acc, ncol = 2)
# 
# ggsave("Exp1_Behavior.tiff", units="in", width=12, height=4, dpi=500, compression = 'lzw')

```






