---
title: "CA costs - Experiment 3"
author: "Ivan Grahek"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## About the code

Experiment: Control adjustment costs Experiment 3 (Speed vs. Accuracy conditions)
Code written by: Ivan Grahek (2023)
Description: Code for the analysis of behavioral data for Experiment 3 of the Control adjustment costs project.  

\newpage

# Load the libraries 


```{r, message=FALSE}
# clear the environment
rm(list=ls()) 

# set seed
set.seed(42) 

#load packages and install them if they're not installed. the pacman package will 
#automatically check for the requested packages and download & install them if they are not on the computer.
if (!require("pacman")) install.packages("pacman")
pacman::p_load(brms,here,broom,knitr,tidyverse,plyr,cowplot,emmeans,tidybayes,grDevices,viridis,MASS)

# Define the summary posterior function
summarize_posterior <- function(model,variable) {
   post = posterior_samples(model, "^b")
   ggplot(post,aes_string(x=paste0("`",variable,"`"))) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(variable,"p<0 = ",length(subset(post[[variable]],post[[variable]]<0))/length(post[[variable]]))) +
     theme_classic() 

}

# Define the difference summary posterior function
summarize_difference_posterior <- function(V1,V2,effect) {
   post = as.data.frame(V1-V2)
   ggplot(data=post,aes(x=`V1 - V2`)) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(effect,"p<0 = ",length(post[post<0])/length(post$`V1 - V2`))) +
     theme_classic() 

}

# Define the difference summary posterior function
summarize_one_posterior <- function(V1,effect) {
   post = as.data.frame(V1)
   ggplot(data=post,aes(x=`V1`)) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(effect,"p<0 = ",length(post[post<0])/length(post$`V1`))) +
     theme_classic() 

}

# Define calculate the posterior probabilities function
posterior_probabilities <- function(model) {
   parameter_names = rownames(summary(model)[["fixed"]])
   post_prob = rep(0,length(parameter_names))
   for (i in 1:length(parameter_names)){
     t = hypothesis(model,paste0(parameter_names[i],"<0"))
     post_prob[i] = t$hypothesis$Post.Prob
   }
  return(post_prob)
}

```



# Main analyses

## Reaction times

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.RT.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
pp_check(model,type="dens_overlay_grouped",group="Congruency")
pp_check(model,type="dens_overlay_grouped",group="isi")
pp_check(model,type="dens_overlay_grouped",group="intervalType")
pp_check(model,type="dens_overlay_grouped",group="blockType")
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL

# add a row name column
# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```

#### Make the posterior conditions

```{r, warning=FALSE, message=FALSE}

# Calculate the posteriors per condition
posterior=emmeans(model,specs=~intervalType*blockType*isi)

posteriorConditions = gather_emmeans_draws(posterior)

# Calculate the conditions
Speed_Fixed_250 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Fixed" & isi=="ISI_250")
Speed_Fixed_1000 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Fixed" & isi=="ISI_1000")

Speed_Varying_250 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Varying" & isi=="ISI_250")
Speed_Varying_1000 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Varying" & isi=="ISI_1000")

Accuracy_Fixed_250 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Fixed" & isi=="ISI_250")
Accuracy_Fixed_1000 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Fixed" & isi=="ISI_1000")

Accuracy_Varying_250 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Varying" & isi=="ISI_250")
Accuracy_Varying_1000 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Varying" & isi=="ISI_1000")
```

#### Speed

```{r, warning=FALSE, message=FALSE}
# Speed goal
Speed_250 = Speed_Fixed_250$.value - Speed_Varying_250$.value
Speed_1000 = Speed_Fixed_1000$.value - Speed_Varying_1000$.value

Speed =Speed_250 - Speed_1000
Speed = as.data.frame(Speed)
h = (hypothesis(Speed,"Speed>0"))
kable(as.data.frame(h$hypothesis),caption="Speed (varying vs. fixed) x (250 vs 1000ms)")

hist(Speed$Speed,col="lightblue", main="Speed goal: (varying vs. fixed) x (250 vs 1000ms)", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Speed (SOA=250ms)

```{r, warning=FALSE, message=FALSE}
# Speed goal
Speed_250 = Speed_Fixed_250$.value - Speed_Varying_250$.value

Speed_250 = as.data.frame(Speed_250)
h = (hypothesis(Speed_250,"Speed_250>0"))
kable(as.data.frame(h$hypothesis),caption="Speed [250ms]")

hist(Speed_250$Speed_250,col="lightblue", main="Speed goal: 250ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Speed (SOA=1000ms)

```{r, warning=FALSE, message=FALSE}
# Speed goal
Speed_1000 = Speed_Fixed_1000$.value - Speed_Varying_1000$.value

Speed_1000 = as.data.frame(Speed_1000)
h = (hypothesis(Speed_1000,"Speed_1000>0"))
kable(as.data.frame(h$hypothesis),caption="Speed [1000ms]")

hist(Speed_1000$Speed_1000,col="lightblue", main="Speed goal: 1000ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Accuracy

```{r, warning=FALSE, message=FALSE}

# Accuracy goal
Accuracy_250 = Accuracy_Fixed_250$.value - Accuracy_Varying_250$.value
Accuracy_1000 = Accuracy_Fixed_1000$.value - Accuracy_Varying_1000$.value

Accuracy =Accuracy_250 - Accuracy_1000
Accuracy = as.data.frame(Accuracy)
h = (hypothesis(Accuracy,"Accuracy<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy (varying vs. fixed) x (250 vs 1000ms)")


hist(Accuracy$Accuracy,col="lightblue", main="Accuracy goal: (varying vs. fixed) x (250 vs 1000ms)", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)
```



#### Accuracy (SOA=250ms)

```{r, warning=FALSE, message=FALSE}
# Accuracy goal
Accuracy_250 = Accuracy_Fixed_250$.value - Accuracy_Varying_250$.value

Accuracy_250 = as.data.frame(Accuracy_250)
h = (hypothesis(Accuracy_250,"Accuracy_250>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy [250ms]")

hist(Accuracy_250$Accuracy_250,col="lightblue", main="Accuracy goal: 250ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Accuracy (SOA=1000ms)

```{r, warning=FALSE, message=FALSE}
# Accuracy goal
Accuracy_1000 = Accuracy_Fixed_1000$.value - Accuracy_Varying_1000$.value

Accuracy_1000 = as.data.frame(Accuracy_1000)
h = (hypothesis(Accuracy_1000,"Accuracy_1000>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy [1000ms]")

hist(Accuracy_1000$Accuracy_1000,col="lightblue", main="Accuracy goal: 1000ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

### Plotting the  model

```{r, warning=FALSE, message=FALSE, fig.width=12,fig.height=5}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                            "b_intervalTypeSpeed_min_Accuracy",
                                            "b_blockTypeVarying_min_Fixed",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeVarying_min_Fixed",
                                            "b_isi1000_min_250",
                                            "b_isi1000_min_250:intervalTypeSpeed_min_Accuracy",
                                            "b_isi1000_min_250:blockTypeVarying_min_Fixed",
                                            "b_isi1000_min_250:intervalTypeSpeed_min_Accuracy:blockTypeVarying_min_Fixed"))
# Remove the non-necessary variables
posterior = posterior[,1:8]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Transform the posteriors
Speed_min_Accuracy = cbind(c(1,1),contr.sdif(2))
Varying_min_Fixed = cbind(c(1,1),contr.sdif(2))
SOA_250_min_1000 = cbind(c(1,1),contr.sdif(2))
coding.total = as.matrix(Speed_min_Accuracy) %x% as.matrix(Varying_min_Fixed) %x% as.matrix(SOA_250_min_1000)

# Create predictions from all the posterior samples
results =  as.data.frame(t(coding.total %*% t(posterior)))

colnames(results) = c("Speed_Varying_SOA1000",
                      "Accuracy_Varying_SOA1000",
                      "Speed_Fixed_SOA1000",
                      "Accuracy_Fixed_SOA1000",
                      "Speed_Varying_SOA250",
                      "Accuracy_Varying_SOA250",
                      "Speed_Fixed_SOA250",
                      "Accuracy_Fixed_SOA250")

results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Block Type',"SOA"),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Speed", "Accuracy"))


# Plot
p = ggplot(results,aes(x=`SOA`,y=Estimate,linetype=`Block Type`,shape=`Block Type`,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) +
  guides(color = guide_legend(override.aes=list(shape = 20)))+
  ylab("Reaction time (ms)")+
  xlab("SOA")+
  scale_x_discrete(labels = c("250ms","1000ms"), expand=c(0.2,0.2))+
  scale_y_continuous(limits = c(670,810))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  
  facet_grid(cols=vars(`Interval Type`))+
  
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(linewidth=0.5),
        axis.line.y.left=element_line(linewidth=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        legend.background = element_rect(fill = "transparent", color = NA))  

p

Fig4.RT = p



```



## Accuracy

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.Acc.rds")



```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
pp_check(model,type="dens_overlay_grouped",group="Congruency")
pp_check(model,type="dens_overlay_grouped",group="isi")
pp_check(model,type="dens_overlay_grouped",group="intervalType")
pp_check(model,type="dens_overlay_grouped",group="blockType")
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL


# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```

#### Make the posterior conditions

```{r, warning=FALSE, message=FALSE}

# Calculate the posteriors per condition
posterior=emmeans(model,specs=~intervalType*blockType*isi)

posteriorConditions = gather_emmeans_draws(posterior)

# Calculate the conditions
Speed_Fixed_250 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Fixed" & isi=="ISI_250")
Speed_Fixed_1000 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Fixed" & isi=="ISI_1000")

Speed_Varying_250 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Varying" & isi=="ISI_250")
Speed_Varying_1000 = subset(posteriorConditions,intervalType=="Speed" & blockType=="Varying" & isi=="ISI_1000")

Accuracy_Fixed_250 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Fixed" & isi=="ISI_250")
Accuracy_Fixed_1000 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Fixed" & isi=="ISI_1000")

Accuracy_Varying_250 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Varying" & isi=="ISI_250")
Accuracy_Varying_1000 = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Varying" & isi=="ISI_1000")
```

#### Speed goal

```{r, warning=FALSE, message=FALSE}
# Speed goal
Speed_250 = Speed_Fixed_250$.value - Speed_Varying_250$.value
Speed_1000 = Speed_Fixed_1000$.value - Speed_Varying_1000$.value

Speed =Speed_250 - Speed_1000
Speed = as.data.frame(Speed)
h = (hypothesis(Speed,"Speed>0"))
kable(as.data.frame(h$hypothesis),caption="Speed (varying vs. fixed) x (250 vs 1000ms)")

hist(Speed$Speed,col="lightblue", main="Speed goal: (varying vs. fixed) x (250 vs 1000ms)", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

# Speed goal

```{r, warning=FALSE, message=FALSE}
Speed_250 = Speed_Fixed_250$.value - Speed_Varying_250$.value

Speed_250 = as.data.frame(Speed_250)
h = (hypothesis(Speed_250,"Speed_250>0"))
kable(as.data.frame(h$hypothesis),caption="Speed [250ms]")

hist(Speed_250$Speed_250,col="lightblue", main="Speed goal: 250ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Speed (SOA=1000ms)

```{r, warning=FALSE, message=FALSE}
# Speed goal
Speed_1000 = Speed_Fixed_1000$.value - Speed_Varying_1000$.value

Speed_1000 = as.data.frame(Speed_1000)
h = (hypothesis(Speed_1000,"Speed_1000>0"))
kable(as.data.frame(h$hypothesis),caption="Speed [1000ms]")

hist(Speed_1000$Speed_1000,col="lightblue", main="Speed goal: 1000ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Accuracy goal: (varying vs. fixed) x (250 vs. 1000ms)

```{r, warning=FALSE, message=FALSE}

# Accuracy goal
Accuracy_250 = Accuracy_Fixed_250$.value - Accuracy_Varying_250$.value
Accuracy_1000 = Accuracy_Fixed_1000$.value - Accuracy_Varying_1000$.value

Accuracy =Accuracy_250 - Accuracy_1000
Accuracy = as.data.frame(Accuracy)
h = (hypothesis(Accuracy,"Accuracy<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy (varying vs. fixed) x (250 vs 1000ms)")


hist(Accuracy$Accuracy,col="lightblue", main="Accuracy goal: (varying vs. fixed) x (250 vs 1000ms)", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)
```

#### Accuracy (SOA=250ms)

```{r, warning=FALSE, message=FALSE}
# Accuracy goal
Accuracy_250 = Accuracy_Fixed_250$.value - Accuracy_Varying_250$.value

Accuracy_250 = as.data.frame(Accuracy_250)
h = (hypothesis(Accuracy_250,"Accuracy_250<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy [250ms]")

hist(Accuracy_250$Accuracy_250,col="lightblue", main="Accuracy goal: 250ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```

#### Accuracy (SOA=1000ms)

```{r, warning=FALSE, message=FALSE}
# Accuracy goal
Accuracy_1000 = Accuracy_Fixed_1000$.value - Accuracy_Varying_1000$.value

Accuracy_1000 = as.data.frame(Accuracy_1000)
h = (hypothesis(Accuracy_1000,"Accuracy_1000<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy [1000ms]")

hist(Accuracy_1000$Accuracy_1000,col="lightblue", main="Accuracy goal: 1000ms", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)

```


### Plotting the  model

```{r, warning=FALSE, message=FALSE, fig.width=12,fig.height=5}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                            "b_intervalTypeSpeed_min_Accuracy",
                                            "b_blockTypeVarying_min_Fixed",
                                            "b_intervalTypeSpeed_min_Accuracy:blockTypeVarying_min_Fixed",
                                            "b_isi1000_min_250",
                                            "b_isi1000_min_250:intervalTypeSpeed_min_Accuracy",
                                            "b_isi1000_min_250:blockTypeVarying_min_Fixed",
                                            "b_isi1000_min_250:intervalTypeSpeed_min_Accuracy:blockTypeVarying_min_Fixed"))
# Remove the non-necessary variables
posterior = posterior[,1:8]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Transform the posteriors
Speed_min_Accuracy = cbind(c(1,1),contr.sdif(2))
Varying_min_Fixed = cbind(c(1,1),contr.sdif(2))
SOA_250_min_1000 = cbind(c(1,1),contr.sdif(2))
coding.total = as.matrix(Speed_min_Accuracy) %x% as.matrix(Varying_min_Fixed) %x% as.matrix(SOA_250_min_1000)

# Create predictions from all the posterior samples
results =  as.data.frame(t(coding.total %*% t(posterior)))

colnames(results) = c("Speed_Varying_SOA1000",
                      "Accuracy_Varying_SOA1000",
                      "Speed_Fixed_SOA1000",
                      "Accuracy_Fixed_SOA1000",
                      "Speed_Varying_SOA250",
                      "Accuracy_Varying_SOA250",
                      "Speed_Fixed_SOA250",
                      "Accuracy_Fixed_SOA250")

results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Block Type',"SOA"),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Speed", "Accuracy"))

# Turn logits into probabilities
results$Estimate = exp(results$Estimate)
results$Estimate = results$Estimate / (1 + results$Estimate)

results$Q2.5 = exp(results$Q2.5)
results$Q2.5 = results$Q2.5 / (1 + results$Q2.5)

results$Q97.5 = exp(results$Q97.5)
results$Q97.5 = results$Q97.5 / (1 + results$Q97.5)


# Plot
p = ggplot(results,aes(x=`SOA`,y=Estimate,linetype=`Block Type`,shape=`Block Type`,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) +
  guides(color = guide_legend(override.aes=list(shape = 20)))+
  ylab("Accuracy")+
  xlab("SOA")+
  scale_x_discrete(labels = c("250ms","1000ms"), expand=c(0.2,0.2))+
  scale_y_continuous(limits = c(0.76,1),breaks = c(0.7,0.8,0.9,1))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  
  facet_grid(cols=vars(`Interval Type`))+
  
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(linewidth=0.5),
        axis.line.y.left=element_line(linewidth=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none",
        legend.background = element_rect(fill = "transparent", color = NA))  

p

Fig4.Acc = p

```





## Save the figures


```{r, warning=FALSE, message=FALSE}

pdf(file="../../../Manuscript/figures/Figure_4_behavior.pdf",height=6,width=22)

p = cowplot::plot_grid(Fig4.RT,
                       Fig4.Acc,
                       nrow = 1)
p
dev.off()

```
