---
title: "Mini Meta Analysis (Effects across 4 studies)"
author: "Ivan Grahek"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## About the code

Experiment: Control adjustment costs - 4 experiments
Code written by: Ivan Grahek (2023)
Description: Code for generating the forest plot with the main effects across 4 studies 

\newpage

# Load the libraries 


```{r, message=FALSE}
# clear the environment
rm(list=ls()) 

# set seed
set.seed(42) 

#load packages and install them if they're not installed. the pacman package will 
#automatically check for the requested packages and download & install them if they are not on the computer.
if (!require("pacman")) install.packages("pacman")
pacman::p_load(brms,here,broom,knitr,tidyverse,plyr,cowplot,emmeans,tidybayes,viridis,MASS)


```



# Enter the effects


```{r,warning=T, message=T}

# Study 1
# Create a data frame
Study1 = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study1_Fix", "Study1_Var","Study1_Cost", "Study1_Fix", "Study1_Var","Study1_Cost"),
  Mean = c(0.56, 0.51, 0.05,0.46, 0.38,0.08),
  CI_lower = c(0.34, 0.29,-0.11, 0.33, 0.25,0.03),
  CI_upper = c(0.79, 0.74, 0.21,0.60, 0.52,0.13)
)

# Maintain the order of the y-axis
Study1$Effect = factor(Study1$Effect, levels = rev(unique(Study1$Effect)))

# Create the forest plot
ggplot(Study1, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

# Study 2
# Create a data frame
Study2_AS = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study2_Fix_A-S", "Study2_Var_A-S","Study2_Cost_A-S","Study2_Fix_A-S", "Study2_Var_A-S","Study2_Cost_A-S"),
  Mean = c(0.84,0.48,0.36,0.54,0.43,0.11),
  CI_lower = c(0.63,0.27,0.16,0.43,0.32,0.04),
  CI_upper = c(1.06,0.70,0.55,0.64,0.53,0.18)
)

Study2_A_AS = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study2_Fix_A-AS", "Study2_Var_A-AS","Study2_Cost_A-AS","Study2_Fix_A-AS", "Study2_Var_A-AS","Study2_Cost_A-AS"),
  Mean = c(0.32,0.23,0.09,0.22,0.18,0.04),
  CI_lower = c(0.11,0.03,-0.09,0.12,0.08,-0.03),
  CI_upper = c(0.52,0.44,0.27,0.33,0.29,0.11)
)

Study2_AS_SS = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study2_Fix_AS-S", "Study2_Var_AS-S","Study2_Cost_AS-S","Study2_Fix_AS-S", "Study2_Var_AS-S","Study2_Cost_AS-S"),
  Mean = c(0.52,0.25,0.27,0.31,0.24,0.07),
  CI_lower = c(0.36,0.08,0.03,0.23,0.16,0.01),
  CI_upper = c(0.69,0.43,0.51,0.39,0.32,0.12)
)

Study2 = rbind(Study2_AS,Study2_AS_SS,Study2_A_AS)

# Maintain the order of the y-axis
Study2$Effect = factor(Study2$Effect, levels = rev(unique(Study2$Effect)))

# Create the forest plot
ggplot(Study2, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")


# Study 3
# Create a data frame
Study3_AS_250 = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study3_Fix_A-S_250", "Study3_Var_A-S_250","Study3_Cost_A-S_250","Study3_Fix_A-S_250", "Study3_Var_A-S_250","Study3_Cost_A-S_250"),
  Mean = c(0.13,0.14,-0.01,0.25,0.14,0.11),
  CI_lower = c(0.00,0.02,-0.17,0.19,0.08,0.06),
  CI_upper = c(0.25,0.27,0.13,0.31,0.20,0.15)
)

Study3_AS_1000 = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study3_Fix_A-S_1000", "Study3_Var_A-S_1000","Study3_Cost_A-S_1000","Study3_Fix_A-S_1000", "Study3_Var_A-S_1000","Study3_Cost_A-S_1000"),
  Mean = c(0.19,0.11,0.07,0.18,0.15,0.03),
  CI_lower = c(0.06,-0.01,-0.08,0.13,0.09,-0.01),
  CI_upper = c(0.31,0.24,0.23,0.24,0.21,0.08)
)
Study3 = rbind(Study3_AS_250,Study3_AS_1000)

# Maintain the order of the y-axis
Study3$Effect = factor(Study3$Effect, levels = rev(unique(Study3$Effect)))

# Create the forest plot
ggplot(Study3, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")



# Study 4
# Create a data frame
Study4 = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold", "Threshold"),
  Effect = c("Study4_Fix", "Study4_8","Study4_4", "Study4_2", "Study4_Fix", "Study4_8","Study4_4", "Study4_2"),
  Mean = c(0.36, 0.41, 0.22, 0.22, 0.31, 0.24, 0.20, 0.19),
  CI_lower = c(0.20,0.27, 0.07, 0.07, 0.24, 0.17, 0.14, 0.13),
  CI_upper = c(0.52,0.56, 0.36, 0.38, 0.37, 0.30, 0.26, 0.26)
)

# Create a data frame
Study4Cost = data.frame(
  # Study = c("Study1", "Study1", "Study1", "Study1"),
  # Block = c("Fixed", "Varying", "Fixed", "Varying"),
  Parameter = c("Drift", "Drift", "Drift", "Threshold", "Threshold", "Threshold"),
  # Effect = c("Study4_8_Cost", "Study4_4_Cost", "Study4_2_Cost","Study4_8_Cost","Study4_4_Cost", "Study4_2_Cost"),
  Effect = c("Study4_2_Cost", "Study4_4_Cost", "Study4_8_Cost","Study4_2_Cost","Study4_4_Cost", "Study4_8_Cost"),
  # Mean = c(-0.05,0.14,0.14, 0.07,0.10,0.11),
  Mean = c(0.14,0.14,-0.05, 0.11,0.10,0.07),
  # CI_lower = c(-0.20, -0.02, -0.05, 0.02,0.05,0.05),
  CI_lower = c(-0.05, -0.02, -0.20, 0.05,0.05,0.02),
  # CI_upper = c(0.10,0.31, 0.32,0.12,0.16,0.17)
  CI_upper = c(0.32,0.31, 0.10,0.17,0.16,0.12)
)
# Maintain the order of the y-axis
Study4$Effect = factor(Study4$Effect, levels = rev(unique(Study4$Effect)))
Study4Cost$Effect = factor(Study4Cost$Effect, levels = rev(unique(Study4Cost$Effect)))

Study4 = rbind(Study4,Study4Cost)





# Create the forest plot
ggplot(Study4, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

```

# Plot all effects together

```{r, warning=FALSE, message=FALSE}
Effects = rbind(Study1,Study2,Study3,Study4)
Effects$Effect = factor(Effects$Effect, levels = rev(unique(Effects$Effect)))

# Create the forest plot
ggplot(Effects, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Enter the distances


```{r,warning=T, message=T}

# Study 1
# Create a data frame
Study1Distance = data.frame(
  Parameter = c("Distance"),
  Effect = c("Control Adjustment Cost"),
  Mean = c(0.09),
  CI_lower = c(-0.05),
  CI_upper = c(0.23)
)

# Study 2
# Create a data frame
Study2Distance = data.frame(
  Parameter = c("Distance","Distance","Distance"),
  Effect = c("Cost (Low distance)","Cost (Medium distance)","Cost (High distance)"),
  Mean = c(0.09,0.25,0.35),
  CI_lower = c(-0.09,0.01,0.15),
  CI_upper = c(0.27,0.48,0.55)
)

# Study 3
# Create a data frame
Study3Distance = data.frame(
  Parameter = c("Distance","Distance"),
  Effect = c("Cost (Long time)","Cost (Short time)"),
  Mean = c(0.08,0.07),
  CI_lower = c(-0.05,-0.06),
  CI_upper = c(0.20,0.21)
)

# Study 4
# Create a data frame
Study4Distance = data.frame(
  Parameter = c("Distance","Distance","Distance"),
  Effect = c("Cost (Low switch frequency)",
                               "Cost (Medium switch frequency)",
                               "Cost (High switch frequency)"),
  Mean = c(0.00,0.17,0.17),
  CI_lower = c(-0.16,0.01,-0.01),
  CI_upper = c(0.16,0.34,0.35)
)


Studies_Distance = rbind(Study1Distance,Study2Distance,Study3Distance,Study4Distance)
Studies_Distance$Effect = factor(Studies_Distance$Effect, levels = rev(unique(Studies_Distance$Effect)))



# Create the forest plot
ggplot(Studies_Distance, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")



```

# Plot all effects together

```{r, warning=FALSE, message=FALSE}
Effects = rbind(Study1,Study2,Study3,Study4)
Effects$Effect = factor(Effects$Effect, levels = rev(unique(Effects$Effect)))

# Create the forest plot
ggplot(Effects, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper), height = 0.1) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~Parameter)+
  labs(title = "Forest Plot", x = "Mean", y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```


# Plot only the costs

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

# Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
# Costs$Effect = factor(Costs$Effect, levels = rev(unique(Costs$Effect)))

Costs$Parameter = factor(Costs$Parameter, levels = c("Threshold", "Drift"))

# Create the forest plot

# Save the figure
pdf(file="../../Manuscript/figures/Figure_6.pdf",height=10,width=12)

p = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  facet_wrap(~Parameter, scales = "free_x")+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p
dev.off()




```

# Plot only the costs (Threshold)

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

# Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
# Costs$Effect = factor(Costs$Effect, levels = rev(unique(Costs$Effect)))

Costs = subset(Costs,Parameter=="Threshold")
# Create the forest plot

# Save the figure
pdf(file="../../Manuscript/figures/Figure_6A.pdf",height=10,width=8)

p = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  xlim(-0.1,0.2)+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p
dev.off()




```

# Plot only the costs (Drift)

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

# Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
# Costs$Effect = factor(Costs$Effect, levels = rev(unique(Costs$Effect)))

Costs = subset(Costs,Parameter=="Drift")
# Create the forest plot

# Save the figure
pdf(file="../../Manuscript/figures/Figure_6B.pdf",height=10,width=8)

p = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  xlim(-0.2,0.59)+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p
dev.off()




```

# Study 1

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
rownames(Costs) = seq(length=nrow(Costs))

Costs = Costs[c(1:2),]

Costs$Effect = c("Study1T1","Study1D2")


# Create the forest plot
p1 = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  xlim(-0.2,0.6)+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p1


```

# Study 2

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
rownames(Costs) = seq(length=nrow(Costs))

Costs = Costs[c(3:8),]

Costs$Effect = c("Study2T1","Study2D2","Study2T3","Study2D4","Study2T5","Study2D6")

# Create the forest plot
p2 = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  xlim(-0.2,0.6)+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p2
```


# Study 3

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
rownames(Costs) = seq(length=nrow(Costs))

Costs = Costs[c(9:12),]
Costs$Effect = c("Study3T1","Study3D2","Study3T3","Study3D4")



# Create the forest plot
p3 = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  xlim(-0.2,0.6)+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p3
```

# Study 4

```{r, warning=FALSE, message=FALSE}
Costs = Effects[c(3,6,9,12,15,18, 21, 24,27,30,33,36,45,46,47,48,49,50),]

Costs$Effect = paste0(Costs$Effect,"_",Costs$Parameter)
rownames(Costs) = seq(length=nrow(Costs))

Costs = Costs[c(13:18),]

Costs$Effect = c("Study4T1","Study4D2","Study4T3","Study4D4","Study4T5","Study4D6")



# Create the forest plot
p4 = ggplot(Costs, aes(x = Mean, y = Effect)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = CI_lower, xmax = CI_upper),height=0) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  ylab("Cost") + 
  xlab("Regression estimate") + 
  xlim(-0.2,0.6)+
    theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  
p4
```

# Save the figures


```{r, message=FALSE}

# Save the figure
pdf(file="../../Manuscript/figures/Figure_6A.pdf",height=2,width=9)
p1
dev.off()

pdf(file="../../Manuscript/figures/Figure_6B.pdf",height=6,width=9)
p2
dev.off()

pdf(file="../../Manuscript/figures/Figure_6C.pdf",height=4,width=9)
p3
dev.off()

pdf(file="../../Manuscript/figures/Figure_6D.pdf",height=6,width=9)
p4
dev.off()




```