---
title: "CA costs - Experiment 1"
author: "Ivan Grahek"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## About the code

Experiment: Control adjustment costs Experiment 1 (Speed vs. Accuracy conditions)
Code written by: Ivan Grahek (2022)
Description: Code for the analysis of behavioral data for Experiment 1 of the Control adjustment costs project.  

\newpage

# Load the libraries 


```{r, message=FALSE}
# clear the environment
rm(list=ls()) 

# set seed
set.seed(42) 

#load packages and install them if they're not installed. the pacman package will 
#automatically check for the requested packages and download & install them if they are not on the computer.
if (!require("pacman")) install.packages("pacman")
pacman::p_load(brms,here,broom,knitr,tidyverse,plyr,cowplot,emmeans,tidybayes,viridis,MASS)

# Define the summary posterior function
summarize_posterior <- function(model,variable) {
   post = posterior_samples(model, "^b")
   ggplot(post,aes_string(x=paste0("`",variable,"`"))) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(variable,"p<0 = ",length(subset(post[[variable]],post[[variable]]<0))/length(post[[variable]]))) +
     theme_classic() 

}

# Define the difference summary posterior function
summarize_difference_posterior <- function(V1,V2,effect) {
   post = as.data.frame(V1-V2)
   ggplot(data=post,aes(x=`V1 - V2`)) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(effect,"p<0 = ",length(post[post<0])/length(post$`V1 - V2`))) +
     theme_classic() 

}

# Define calculate the posterior probabilities function
posterior_probabilities <- function(model) {
   parameter_names = rownames(summary(model)[["fixed"]])
   post_prob = rep(0,length(parameter_names))
   for (i in 1:length(parameter_names)){
     t = hypothesis(model,paste0(parameter_names[i],"<0"))
     post_prob[i] = t$hypothesis$Post.Prob
   }
  return(post_prob)
}

```



# Main analyses

## Reaction times

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.RT.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL

# add a row name column
# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```

#### Make the posterior conditions

```{r, warning=FALSE, message=FALSE}

# Calculate the posteriors per condition
posterior=emmeans(model,specs=~intervalType|blockType,epred = TRUE)

posteriorConditions = gather_emmeans_draws(posterior)

# Calculate the conditions
Speed_Fixed = subset(posteriorConditions,intervalType=="Speed" & blockType=="Fixed")
posterior_summary(Speed_Fixed$.value)
Speed_Varying = subset(posteriorConditions,intervalType=="Speed" & blockType=="Mixed")
posterior_summary(Speed_Varying$.value)

Accuracy_Fixed = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Fixed")
Accuracy_Varying = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Mixed")


# 
# # Create a matrix
# p1 = ddply(p1,.(blockType,intervalType),plyr::summarize,
#                       estimate__ = posterior_summary(Estimate)[1],
#                       lower__ = posterior_summary(Estimate)[3],
#                       upper__ = posterior_summary(Estimate)[4])




# Default plot
p = conditional_effects(model, effects = "intervalType:blockType")

# Convert to a data frame
p = as.data.frame(p$`intervalType:blockType`)
p

```

#### Comparing the conditions

Speed goal

```{r, warning=FALSE, message=FALSE}

# Speed goal
Speed_Goal = Speed_Varying$.value - Speed_Fixed$.value
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed (varying vs. fixed)")

hist(Speed_Goal$Speed_Goal,col="lightblue", main="Speed goal: Varying - Fixed", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

Accuracy goal

```{r, warning=FALSE, message=FALSE}

# Accuracy goal
Accuracy_Goal = Accuracy_Varying$.value - Accuracy_Fixed$.value
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy (varying vs. fixed)")

hist(Accuracy_Goal$Accuracy_Goal,col="lightblue", main="Accuracy goal: Varying - Fixed", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

### Plotting the  model

```{r, warning=FALSE, message=FALSE}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                              "b_intervalTypeSpeed_min_Accuracy",
                                              "b_blockTypeMixed_min_Fixed",
                                              "b_intervalTypeSpeed_min_Accuracy:blockTypeMixed_min_Fixed"))
# Remove the non-necessary variables
posterior = posterior[,1:4]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Transform the posteriors
Speed_min_Accuracy = cbind(c(1,1),contr.sdif(2))
Mixed_min_Fixed = cbind(c(1,1),contr.sdif(2))
coding.total = as.matrix(Speed_min_Accuracy) %x% as.matrix(Mixed_min_Fixed)

# Create predictions from all the posterior samples
results =  as.data.frame(t(coding.total %*% t(posterior)))
colnames(results) = c("Speed_Varying","Accuracy_Varying","Speed_Fixed","Accuracy_Fixed")

results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Block Type'),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Speed", "Accuracy"))

# Plot
p = ggplot(results, aes(x = `Interval Type`, y = Estimate, linetype = `Block Type`, shape = `Block Type`, color = `Interval Type`)) +
  geom_pointrange(aes(ymin = Q2.5, ymax = Q97.5), position = position_dodge(0.4), size = 2, fatten = 2) +
  guides(color = guide_legend(override.aes = list(shape = 20))) +
  ylab("Reaction times (ms)") +
  xlab("Performance goal") +
  scale_x_discrete(labels = c("Speed", "Accuracy"), expand = c(0.2, 0.2)) +
  scale_y_continuous(limits = c(600,810))+
  scale_color_viridis(discrete = TRUE, option = "plasma", end = 0.7) +
  
  theme(axis.line = element_line(colour = "black"),
        plot.margin = grid::unit(c(5, 85, 5, 5), "mm"),
        axis.line.x.bottom = element_line(size = 0.5),
        axis.line.y.left = element_line(size = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size = 33, color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  

p


Fig2.RT = p


```








## Accuracy

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.Acc.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL


# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```


#### Make the posterior conditions

```{r, warning=FALSE, message=FALSE}

# Calculate the posteriors per condition
posterior=emmeans(model,specs=~intervalType*blockType)

posteriorConditions = gather_emmeans_draws(posterior)

# Calculate the conditions
Speed_Fixed = subset(posteriorConditions,intervalType=="Speed" & blockType=="Fixed")
Speed_Varying = subset(posteriorConditions,intervalType=="Speed" & blockType=="Mixed")
Accuracy_Fixed = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Fixed")
Accuracy_Varying = subset(posteriorConditions,intervalType=="Accuracy" & blockType=="Mixed")
```

#### Comparing the conditions

Speed goal

```{r, warning=FALSE, message=FALSE}

# Speed goal
Speed_Goal = Speed_Varying$.value - Speed_Fixed$.value
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed (varying vs. fixed)")

hist(Speed_Goal$Speed_Goal,col="lightblue", main="Speed goal: Varying - Fixed", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

Accuracy goal

```{r, warning=FALSE, message=FALSE}

# Accuracy goal
Accuracy_Goal = Accuracy_Varying$.value - Accuracy_Fixed$.value
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy (varying vs. fixed)")

hist(Accuracy_Goal$Accuracy_Goal,col="lightblue", main="Accuracy goal: Varying - Fixed", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

### Plotting the  model

```{r, warning=FALSE, message=FALSE}
# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                              "b_intervalTypeSpeed_min_Accuracy",
                                              "b_blockTypeMixed_min_Fixed",
                                              "b_intervalTypeSpeed_min_Accuracy:blockTypeMixed_min_Fixed"))
# Remove the non-necessary variables
posterior = posterior[,1:4]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Transform the posteriors
Speed_min_Accuracy = cbind(c(1,1),contr.sdif(2))
Mixed_min_Fixed = cbind(c(1,1),contr.sdif(2))
coding.total = as.matrix(Speed_min_Accuracy) %x% as.matrix(Mixed_min_Fixed)

# Create predictions from all the posterior samples
results =  as.data.frame(t(coding.total %*% t(posterior)))
colnames(results) = c("Speed_Varying","Accuracy_Varying","Speed_Fixed","Accuracy_Fixed")

results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Block Type'),'_')

# Turn logits into probabilities
results$Estimate = exp(results$Estimate)
results$Estimate = results$Estimate / (1 + results$Estimate)

results$Q2.5 = exp(results$Q2.5)
results$Q2.5 = results$Q2.5 / (1 + results$Q2.5)

results$Q97.5 = exp(results$Q97.5)
results$Q97.5 = results$Q97.5 / (1 + results$Q97.5)

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Speed", "Accuracy"))

# Plot
p = ggplot(results,aes(x=`Interval Type`,y=Estimate,linetype=`Block Type`,shape=`Block Type`,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) + 
  guides(color = guide_legend(
    override.aes=list(shape = 20)))+
  
  # ggtitle("Accuracy")+ 
  ylab("Accuracy")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed","Accuracy"), expand=c(0.2, 0.2))+
  scale_y_continuous(limits = c(0.58,1))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(size=0.5),
        axis.line.y.left=element_line(size=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  

p



Fig2.Acc = p

```





# Switch-Repeat analysis



## Reaction times

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.RTSwitchRepeat.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL

# add a row name column
# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```

#### Make the posterior conditions

```{r, warning=FALSE, message=FALSE}

# Calculate the posteriors per condition
posterior=emmeans(model,specs=~intervalType*Switch)

posteriorConditions = gather_emmeans_draws(posterior)

# Calculate the conditions
Speed_Repeat = subset(posteriorConditions,intervalType=="Speed" & Switch=="Repeat")
Speed_Switch = subset(posteriorConditions,intervalType=="Speed" & Switch=="Switch")
Accuracy_Repeat = subset(posteriorConditions,intervalType=="Accuracy" & Switch=="Repeat")
Accuracy_Switch = subset(posteriorConditions,intervalType=="Accuracy" & Switch=="Switch")
```

#### Comparing the conditions

Speed goal

```{r, warning=FALSE, message=FALSE}

# Speed goal
Speed_Goal = Speed_Switch$.value - Speed_Repeat$.value
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed (switch vs. repeat)")

hist(Speed_Goal$Speed_Goal,col="lightblue", main="Speed goal: Switch - Repeat", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

Accuracy goal

```{r, warning=FALSE, message=FALSE}

# Accuracy goal
Accuracy_Goal = Accuracy_Switch$.value - Accuracy_Repeat$.value
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy (switch vs. repeat)")

hist(Accuracy_Goal$Accuracy_Goal,col="lightblue", main="Accuracy goal: Switch - Repeat", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

### Plotting the  model

```{r, warning=FALSE, message=FALSE}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                              "b_intervalTypeSpeed_min_Accuracy",
                                              "b_SwitchSwitch_min_Repeat",
                                              "b_intervalTypeSpeed_min_Accuracy:SwitchSwitch_min_Repeat"))
# Remove the non-necessary variables
posterior = posterior[,1:4]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Transform the posteriors
Switch_min_Repeat = cbind(c(1,1),contr.sdif(2))
Mixed_min_Fixed = cbind(c(1,1),contr.sdif(2))
coding.total = as.matrix(Speed_min_Accuracy) %x% as.matrix(Switch_min_Repeat)

# Create predictions from all the posterior samples
results =  as.data.frame(t(coding.total %*% t(posterior)))
colnames(results) = c("Speed_Switch","Accuracy_Switch","Speed_Repeat","Accuracy_Repeat")

results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Switch'),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Speed", "Accuracy"))

# Plot
p = ggplot(results,aes(x=`Interval Type`,y=Estimate,linetype=Switch,shape=Switch,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) + 
  guides(color = guide_legend(
  override.aes=list(shape = 20)))+
  ylab("Reaction time (ms)")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed","Accuracy"), expand=c(0.2, 0.2))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  scale_y_continuous(limits = c(600,810))+
  
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(size=0.5),
        axis.line.y.left=element_line(size=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  

p


Fig2.RT_Switch = p

```





## Accuracy

### Import the model

```{r,warning=T, message=T}

model = readRDS("Cluster/output/model.AccSwitchRepeat.rds")

```

### Checks

Plotting the chains
```{r, warning=FALSE, message=FALSE}
# Plot chains
plot(model, pars = "^b_", ask = FALSE, N=4)
```

R hat
```{r, warning=FALSE, message=FALSE}
# R hat for all parameters
stanplot(model, type="rhat_hist")
```


Posterior predictive check
```{r, warning=FALSE, message=FALSE}
# Plot chains
pp_check(model)
```

### Summary of the best model

```{r, warning=FALSE, message=FALSE}
# Summary of the model
x=summary(model)[["fixed"]]
x$`HDI(95%)` = paste(format(round(x$`l-95% CI`, 2), nsmall = 2), format(round(x$`u-95% CI`, 2), nsmall = 2), sep=", ")
x$`l-95% CI` = NULL
x$`u-95% CI` = NULL
x$Bulk_ESS = NULL
x$Rhat = NULL
x$Tail_ESS = NULL

# add a row name column
names = rownames(x)
x = cbind(names,x)
rownames(x) = NULL


# turn into numeric to round
x$Estimate = as.numeric(x$Estimate)
x$Est.Error = as.numeric(x$Est.Error)

# calculate the posterior probabilities
x$PostProb = posterior_probabilities(model)

# edit the column names
kable(x,digits = 2,col.names = c("Parameter", "Estimate", "SE", "CI (95%)","p<0"),align = "lrrrr")

```

#### Make the posterior conditions

```{r, warning=FALSE, message=FALSE}

# Calculate the posteriors per condition
posterior=emmeans(model,specs=~intervalType*Switch)

posteriorConditions = gather_emmeans_draws(posterior)

# Calculate the conditions
Speed_Repeat = subset(posteriorConditions,intervalType=="Speed" & Switch=="Repeat")
Speed_Switch = subset(posteriorConditions,intervalType=="Speed" & Switch=="Switch")
Accuracy_Repeat = subset(posteriorConditions,intervalType=="Accuracy" & Switch=="Repeat")
Accuracy_Switch = subset(posteriorConditions,intervalType=="Accuracy" & Switch=="Switch")
```

#### Comparing the conditions

Speed goal

```{r, warning=FALSE, message=FALSE}

# Speed goal
Speed_Goal = Speed_Switch$.value - Speed_Repeat$.value
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed (switch vs. repeat)")

hist(Speed_Goal$Speed_Goal,col="lightblue", main="Speed goal: Switch - Repeat", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

Accuracy goal

```{r, warning=FALSE, message=FALSE}

# Accuracy goal
Accuracy_Goal = Accuracy_Switch$.value - Accuracy_Repeat$.value
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy (switch vs. repeat)")

hist(Accuracy_Goal$Accuracy_Goal,col="lightblue", main="Accuracy goal: Switch - Repeat", xlab="", breaks = 30)  
abline(v = 0, col="black", lwd=3, lty=2)


```

### Plotting the  model

```{r, warning=FALSE, message=FALSE}

# Extract posteriors
posterior = as_draws_df(model, variable = c("b_Intercept",
                                              "b_intervalTypeSpeed_min_Accuracy",
                                              "b_SwitchSwitch_min_Repeat",
                                              "b_intervalTypeSpeed_min_Accuracy:SwitchSwitch_min_Repeat"))
# Remove the non-necessary variables
posterior = posterior[,1:4]

# Set the intercept to the mean value
posterior$b_Intercept = mean(posterior$b_Intercept)

# Transform the posteriors
Switch_min_Repeat = cbind(c(1,1),contr.sdif(2))
Mixed_min_Fixed = cbind(c(1,1),contr.sdif(2))
coding.total = as.matrix(Speed_min_Accuracy) %x% as.matrix(Switch_min_Repeat)

# Create predictions from all the posterior samples
results =  as.data.frame(t(coding.total %*% t(posterior)))
colnames(results) = c("Speed_Switch","Accuracy_Switch","Speed_Repeat","Accuracy_Repeat")

results = as.data.frame(posterior_summary(results))
results$factor = rownames(results)
results = results %>% separate(factor,c('Interval Type','Switch'),'_')

# Reorder the factor levels
results$`Interval Type` = factor(results$`Interval Type`, levels = c("Speed", "Accuracy"))

# Turn logits into probabilities
results$Estimate = exp(results$Estimate)
results$Estimate = results$Estimate / (1 + results$Estimate)

results$Q2.5 = exp(results$Q2.5)
results$Q2.5 = results$Q2.5 / (1 + results$Q2.5)

results$Q97.5 = exp(results$Q97.5)
results$Q97.5 = results$Q97.5 / (1 + results$Q97.5)


# Plot
p = ggplot(results,aes(x=`Interval Type`,y=Estimate,linetype=Switch,shape=Switch,color=`Interval Type`)) + 
  geom_pointrange(aes(ymin=Q2.5, ymax=Q97.5),position=position_dodge(0.4),size=2, fatten = 2) + 
  guides(color = guide_legend(
  override.aes=list(shape = 20)))+
  ylab("Accuracy")+
  xlab("Performance goal")+
  scale_x_discrete(limits = c("Speed","Accuracy"), expand=c(0.2, 0.2))+
  scale_y_continuous(limits = c(0.58,1))+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,85,5,5), "mm"),
        axis.line.x.bottom=element_line(size=0.5),
        axis.line.y.left=element_line(size=0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
        text = element_text(size=33,color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5,size = 20, face = "bold"),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.8, 0.25),
        legend.background = element_rect(fill = "transparent", color = NA))  

p


Fig2.Acc_Switch = p


```






# Save the figures


```{r, warning=FALSE, message=FALSE}

pdf(file="../../../Manuscript/figures/Figure_2_behavior.pdf",height=12,width=16)

p = cowplot::plot_grid(Fig2.RT,
                       Fig2.Acc,
                       Fig2.RT_Switch,
                       Fig2.Acc_Switch,
                       nrow = 2)
p
dev.off()


```