---
title: "DDM results Experiment 3"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Loading libraries

```{r, message=FALSE}
# test
library(dplyr)
library(ggplot2)
library(purrr)
library(tidyr)
library(gridExtra)
library(cowplot)
library(sjPlot)
library(RColorBrewer)
library(knitr)
library(data.table)
library(grDevices)
library(brms)
library(viridis)


# Functions
test.params <- function(df) {
  inner_join(inner_join(inner_join(df %>%
                                     map_dfr(mean) %>%
                                     gather(parameter, estimate, everything()) %>% dplyr::rename(Mean=estimate),
                                   df %>%
                                     map_dfr(sd) %>%
                                     gather(parameter, estimate, everything()) %>% dplyr::rename(SD=estimate),by='parameter'),
                        
                        df %>% map(~ .x > 0) %>% 
                          map_dfr(mean) %>%
                          gather(parameter, pvalue, everything()) %>%
                          mutate(pvalue = if_else(round(pvalue)==1, 1-pvalue, pvalue),
                                 sig = if_else(pvalue < 0.001, "***",
                                               if_else(pvalue < 0.01, "**",
                                                       if_else(pvalue < 0.05, "*", "n.s."))))),
             inner_join(df %>%
                          map_dfr(function(x) return(quantile(x,0.975)[[1]])) %>%
                          gather(parameter, estimate, everything()) %>% dplyr::rename(CI_upper=estimate),
                        df %>% map_dfr(function(x) return(quantile(x,0.025)[[1]])) %>%
                          gather(parameter, estimate, everything()) %>% dplyr::rename(CI_lower=estimate),by='parameter'),by='parameter') 
}

# Define the summary posterior function
summarize_posterior <- function(V1,V2,effect) {
   post = as.data.frame(V1-V2)
   ggplot(data=post,aes(x=`V1 - V2`)) + 
     geom_histogram(bins=50) + 
     geom_vline(xintercept=0, linetype="dotted",size=1) + 
     labs(title=paste(effect,"p<0 = ",length(post[post<0])/length(post$`V1 - V2`))) +
     theme_classic() 

}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

# Base template
gg <- list(
  theme_bw(),
  theme(plot.title = element_text(hjust = 0.5, size=13),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing = unit(0.75, "lines"),
        legend.box.spacing = unit(0.5, "lines"),
        legend.position = "bottom",
        legend.margin = margin(c(0, 0, 0, 0), unit='lines'))
)

# Density template
ggdensity <- list(
  gg,
  theme(panel.spacing = unit(0.25, "lines"),
        legend.key.size = unit(0.7, "lines"),
        legend.direction = "horizontal",
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.box.spacing = unit(0.25, "lines"))
)
```




# Main analyses - Interval type on NDT


## Rhats

```{r, message=FALSE}
# Import the Rhats
rhats <- fread('output/Mixed/ae_only/modelMixed1/modelMixed1_RHat.csv', header = T)
colnames(rhats) = c("parameter","Rhat")


# Plot the Rhats

# Set parameters for plots
set_theme(base =theme_bw(base_size = 15, base_family = "")) # font size and theme
myColors = brewer.pal(3,"Set2") #colors
barfill <- "#4271AE"
barlines <- "#1F3552"

p =ggplot(rhats, aes(Rhat)) +
  geom_histogram(colour = barlines, fill = barfill,binwidth = 0.01)+ #colour = barlines, fill = barfill
  theme_bw() +
  labs(x = "Rhat", y = "Count\n")+
  theme(axis.line = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
        panel.grid.minor = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 18,  face = "bold",hjust = 0.5),
        text=element_text(colour="black", size = 14),
        axis.text.x=element_text(colour="black", size = 14),
        axis.text.y=element_text(colour="black", size = 14, face = "plain",hjust=0),
        axis.title=element_text(size=18,colour = "black",vjust = 1))

p


# Print the names of the low Rhat parameters
highRhats = subset(rhats,rhats$Rhat>1.1)
highRhats
```



## Trace plots


```{r, message=FALSE}
traces <- read.csv('output/Mixed/ae_only/modelMixed1/modelMixed1_traces.csv')

traces = traces %>% dplyr::select(v_Intercept,
                                 v_C.intervalType..Sum..S.Speed.,
                                 v_C.blockType..Sum..S.Varying.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 v_C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_Intercept,
                                 a_C.intervalType..Sum..S.Speed.,
                                 a_C.blockType..Sum..S.Varying.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 a_C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 t_Intercept)%>%
                          
            mutate(a_Intercept=0.5*a_Intercept,
                   a_C.intervalType..Sum..S.Speed.=0.5*a_C.intervalType..Sum..S.Speed.,
                   a_C.blockType..Sum..S.Varying.=0.5*a_C.blockType..Sum..S.Varying.,
                   a_C.isi..Sum..S.ISI_250.=0.5*a_C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                   a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                   a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)


# For each parameter
colNames= names(traces)

for (parameter in colNames) {

  #Plotting
  plot_data1 = traces[1:2000,]
  plot_data2 = traces[2001:4000,]
  plot_data3 = traces[4001:6000,]
  plot_data4 = traces[6001:8000,]
  plot_data5 = traces[8001:10000,]



  traces_plot = ggplot(NULL) +

    # Chain 1
    geom_line(data=plot_data1,mapping =aes_string(y=parameter,x = 1:2000), colour="red")+

    # Chain 2
    geom_line(data=plot_data2,mapping =aes_string(y=parameter,x = 1:2000), colour="royalblue1")+

    # Chain 3
    geom_line(data=plot_data3,mapping =aes_string(y=parameter,x = 1:2000), colour="springgreen")+

    # Chain 4
    geom_line(data=plot_data4,mapping =aes_string(y=parameter,x = 1:2000), colour="grey0")+

    # Chain 5
    geom_line(data=plot_data5,mapping =aes_string(y=parameter,x = 1:2000), colour="coral")+
    theme_classic(base_size = 18) +

    ggtitle(parameter)  + ylab("Parameter value") + xlab("Sample")



  print(traces_plot)
}
```




## PPCs


```{r, message=FALSE}

df.ppc <- fread('output/Mixed/ae_only/modelMixed1/modelMixed1_simData.csv') %>%
  mutate(simResponse=rt_sampled>0,
         Response=rt>0,
         rt_unsigned = abs(rt),
         rt_sampled_unsigned = abs(rt_sampled))


df.ppc.sim <- df.ppc %>% filter(sample==0,rt_sampled_unsigned<=3)

df.ppc.data <- df.ppc %>% filter(sample==0,rt_unsigned<=3)

ratio.true <- sum(!df.ppc.data$Response)/sum(df.ppc.data$Response)

ratio.simu <- sum(!df.ppc.sim$simResponse)/sum(df.ppc.sim$simResponse)

# Density plots with means
ggplot(df.ppc.data %>% filter(Response),
       aes(x=rt_unsigned,color='Correct',linetype='True')) +
  geom_density(size=1) +
  geom_density(data=df.ppc.data %>% filter(!Response),
               size=1,
               aes(x=rt_unsigned,y=-..density..*ratio.true,color='Incorrect',linetype='True'),
  ) +
  geom_density(data=df.ppc.sim %>% filter(simResponse),
               size=1,
               aes(x=rt_sampled_unsigned,color='Correct',linetype='Simulation')) +
  geom_density(data=df.ppc.sim %>% filter(!simResponse),
               size=1,
               aes(x=rt_sampled_unsigned,y=-..density..*ratio.simu,color='Incorrect',linetype='Simulation'),
  ) + geom_hline(yintercept=0) + ggdensity +
  xlab('Reaction Time') + coord_cartesian(xlim=c(0,2)) + facet_grid(cols=vars(intervalType,blockType,isi)) + scale_linetype_manual(name='Data:',values=c('Simulation'=1,'True'=2)) + scale_color_manual(name='Response:',values=c('Correct'='blue','Incorrect'='red'))
```





## Import the posteriors

### Transform the traces

```{r, message=FALSE}
traces = read.csv('output/Mixed/ae_only/modelMixed1/modelMixed1_traces.csv')


# Drift rates
traces_drift = traces %>% dplyr::select(v_Intercept,
                                 v_C.intervalType..Sum..S.Speed.,
                                 v_C.blockType..Sum..S.Varying.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 v_C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)

traces.mat = t(data.matrix(traces_drift))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_drift = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_drift) = c("Drift_Speed_Varying_ISI250",
                           "Drift_Accuracy_Varying_ISI250",
                           "Drift_Speed_Fixed_ISI250",
                           "Drift_Accuracy_Fixed_ISI250",
                           "Drift_Speed_Varying_ISI1000",
                           "Drift_Accuracy_Varying_ISI1000",
                           "Drift_Speed_Fixed_ISI1000",
                           "Drift_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_drift$Drift_Varying_ISI250 = conditions_drift$Drift_Accuracy_Varying_ISI250 - conditions_drift$Drift_Speed_Varying_ISI250
conditions_drift$Drift_Varying_ISI1000 = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Speed_Varying_ISI1000

conditions_drift$Drift_Fixed_ISI250 = conditions_drift$Drift_Accuracy_Fixed_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
conditions_drift$Drift_Fixed_ISI1000 = conditions_drift$Drift_Accuracy_Fixed_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000




# Thresholds
traces_threshold = traces %>% dplyr::select(a_Intercept,
                                 a_C.intervalType..Sum..S.Speed.,
                                 a_C.blockType..Sum..S.Varying.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 a_C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)%>%
                          
            mutate(a_Intercept=0.5*a_Intercept,
                   a_C.intervalType..Sum..S.Speed.=0.5*a_C.intervalType..Sum..S.Speed.,
                   a_C.blockType..Sum..S.Varying.=0.5*a_C.blockType..Sum..S.Varying.,
                   a_C.isi..Sum..S.ISI_250.=0.5*a_C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                   a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                   a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)


traces.mat = t(data.matrix(traces_threshold))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_threshold = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_threshold) = c("Threshold_Speed_Varying_ISI250",
                           "Threshold_Accuracy_Varying_ISI250",
                           "Threshold_Speed_Fixed_ISI250",
                           "Threshold_Accuracy_Fixed_ISI250",
                           "Threshold_Speed_Varying_ISI1000",
                           "Threshold_Accuracy_Varying_ISI1000",
                           "Threshold_Speed_Fixed_ISI1000",
                           "Threshold_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_threshold$Threshold_Varying_ISI250 = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Speed_Varying_ISI250
conditions_threshold$Threshold_Varying_ISI1000 = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Varying_ISI1000

conditions_threshold$Threshold_Fixed_ISI250 = conditions_threshold$Threshold_Accuracy_Fixed_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
conditions_threshold$Threshold_Fixed_ISI1000 = conditions_threshold$Threshold_Accuracy_Fixed_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000

# Take only the difference variables
# conditions_threshold = conditions_threshold[,9:12]

# First column of condition.mu will be  1 1 1 which means all high, which means Speed, Varying, and ISI_250
# Second column will be -1 1 1 which means Accuracy, Varying, ISI_250

# f,  g,  h
# 1,  1,  1
#-1,  1,  1
# 1, -1,  1
#-1, -1,  1
# 1,  1, -1
#-1,  1, -1
# 1, -1, -1
#-1, -1, -1


  


```

### Summarry of the parameter estimates

```{r, message=FALSE}

# Drift - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_drift$v_C.intervalType..Sum..S.Speed. = traces_drift$v_C.intervalType..Sum..S.Speed.*2
traces_drift$v_C.blockType..Sum..S.Varying. = traces_drift$v_C.blockType..Sum..S.Varying.*2
traces_drift$v_C.isi..Sum..S.ISI_250. = traces_drift$v_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_drift$v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_drift$v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_drift$v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_drift$v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
drift.rate = test.params(traces_drift)

# Print the summary
kable(drift.rate,caption="Drift rate parameter estimates")

# Threshold - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_threshold$a_C.intervalType..Sum..S.Speed. = traces_threshold$a_C.intervalType..Sum..S.Speed.*2
traces_threshold$a_C.blockType..Sum..S.Varying. = traces_threshold$a_C.blockType..Sum..S.Varying.*2
traces_threshold$a_C.isi..Sum..S.ISI_250. = traces_threshold$a_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_threshold$a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_threshold$a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
threshold = test.params(traces_threshold)

# Print the summary
kable(threshold,caption="Threshold parameter estimates")


```

### Summarize the posteriors

```{r, message=FALSE}

drift.rate <- test.params(conditions_drift)
# Take only the difference variables
drift.rate = drift.rate[9:12,]

threshold <- test.params(conditions_threshold)
# Take only the difference variables
threshold = threshold[9:12,]

# NDT<- output %>% filter(parameter %in% c('t_Speed',
#                                          't_Acc'))

va <- rbind(drift.rate,threshold) %>% separate(parameter,c('parameter','fixed','isi'),'_')
va = as.data.frame(va)
va$parameter = as.factor(va$parameter)
va$fixed = as.factor(va$fixed)
va$isi = as.factor(va$isi)
va$isi = ifelse(va$isi=="ISI250", "250", "1000")
va$isi = factor(va$isi,levels=c("250","1000"))


```


## Drift rate and threshold

### Bar plot

```{r, message=FALSE}



# Plot
p<-ggplot(va,aes(x=isi, y=Mean,fill=fixed)) +
  geom_bar(width=0.6,stat="identity", position=position_dodge(0.6)) +
  geom_errorbar(width=.1, size=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower,ymax=CI_upper)) + ylab('Estimate') +
  facet_wrap(vars(parameter), labeller = as_labeller(c('Drift'="Drift rate",'Threshold'="Threshold")))+
  ylim(-0.1,0.4)+
  # labs(x="SOA (ms)")+
  geom_hline(yintercept=0) +
  scale_fill_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  scale_x_discrete(expand = c(0.3,0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0)),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.title.x=element_blank(),
        # axis.text.x = element_text(color="black"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.85, 0.90),
        legend.background = element_rect(fill = "transparent", color = NA))  
        
p

# ggsave("Mixed_ae_only_VAT.tiff", units="in", width=15, height=4, dpi=400, compression = 'lzw')
kable(va)

# Conditions of interest

# Threshold
threshold_Fixed_min_Varying_isi250 = conditions_threshold$Threshold_Fixed_ISI250 - conditions_threshold$Threshold_Varying_ISI250
threshold_Fixed_min_Varying_isi1000 = conditions_threshold$Threshold_Fixed_ISI1000 - conditions_threshold$Threshold_Varying_ISI1000
threshold_Fixed_min_Varying = (threshold_Fixed_min_Varying_isi250 + threshold_Fixed_min_Varying_isi1000)/2
threshold_Acc_min_Speed = (conditions_threshold$Threshold_Fixed_ISI250+
                           conditions_threshold$Threshold_Varying_ISI250+
                           conditions_threshold$Threshold_Fixed_ISI1000+
                           conditions_threshold$Threshold_Varying_ISI1000)/4

#Drift
drift_Fixed_min_Varying_isi250 = conditions_drift$Drift_Fixed_ISI250 - conditions_drift$Drift_Varying_ISI250
drift_Fixed_min_Varying_isi1000 = conditions_drift$Drift_Fixed_ISI1000 - conditions_drift$Drift_Varying_ISI1000
drift_Fixed_min_Varying = (drift_Fixed_min_Varying_isi250 + drift_Fixed_min_Varying_isi1000)/2
drift_Acc_min_Speed = (conditions_drift$Drift_Fixed_ISI250+
                       conditions_drift$Drift_Varying_ISI250+
                       conditions_drift$Drift_Fixed_ISI1000+
                       conditions_drift$Drift_Varying_ISI1000)/4


# Main effects
#---------------------------------------------------------------------------------------
# Threshold - main effect of the condition type
table = test.params(as.data.frame(threshold_Acc_min_Speed))
table[1] = "Threshold (Acc-Speed)"
kable(table)

# Drift - main effect of the condition type
table = test.params(as.data.frame(drift_Acc_min_Speed))
table[1] = "Drift (Acc-Speed)"
kable(table)


# Threshold - Block x condition
table = test.params(as.data.frame(threshold_Fixed_min_Varying))
table[1] = "Threshold (Fixed-Varying) X (Acc-Speed)"
kable(table)

# Drift - Block x condition
table = test.params(as.data.frame(drift_Fixed_min_Varying))
table[1] = "Drift (Fixed-Varying) X (Acc-Speed)"
kable(table)

# Fixed vs. varying
#---------------------------------------------------------------------------------------

# # Threshold - difference between fixed and varying ISI 250
# summarize_posterior(threshold_Fixed_min_Varying_isi250, rep(0,length(threshold_Fixed_min_Varying_isi250)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250))
# table[1] = "Threshold (Fixed-Varying) ISI250"
# kable(table)
# 
# # Threshold - difference between fixed and varying ISI 1000
# summarize_posterior(threshold_Fixed_min_Varying_isi1000, rep(0,length(threshold_Fixed_min_Varying_isi1000)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi1000))
# table[1] = "Threshold (Fixed-Varying) ISI1000"
# kable(table)

# Threshold - difference between 250 and 1000
#summarize_posterior(threshold_Fixed_min_Varying_isi250, threshold_Fixed_min_Varying_isi1000, "Threshold: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250 - threshold_Fixed_min_Varying_isi1000))
table[1] = "Threshold: 3-way interaction"
kable(table)

# # Drift - difference between fixed and varying ISI 250
# summarize_posterior(drift_Fixed_min_Varying_isi250, rep(0,length(drift_Fixed_min_Varying_isi250)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250))
# table[1] = "Drift (Fixed-Varying) ISI250"
# kable(table)
# 
# # Drift - difference between fixed and varying ISI 1000
# summarize_posterior(drift_Fixed_min_Varying_isi1000, rep(0,length(drift_Fixed_min_Varying_isi1000)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi1000))
# table[1] = "Drift (Fixed-Varying) ISI1000"
# kable(table)

# Drift - difference between 250 and 1000
#summarize_posterior(drift_Fixed_min_Varying_isi250, drift_Fixed_min_Varying_isi1000, "drift: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250 - drift_Fixed_min_Varying_isi1000))
table[1] = "Drift: 3-way interaction"
kable(table)


# # Save the figure
# pdf(file="../../../Manuscript/figures/Figure_Exp6_DDM.pdf",height=4,width=8)
# 
# p = cowplot::plot_grid(Exp6.DDM,
#                        nrow = 1)
# p
# dev.off()

```


### Points in 2D 

```{r, message=FALSE}


drift.rate<- test.params(conditions_drift)[1:8,]

threshold<- test.params(conditions_threshold)[1:8,]


va <- rbind(drift.rate,threshold) %>% separate(parameter,c('parameter','factor','fixed','isi'),'_')

va$factor = as.factor(va$factor)

# va$parameter<-factor(va$parameter,labels=c('Threshold','Drift Rate'))


# data = subset(va,fixed=="Varying")
# data = subset(va,isi=="ISI250")

data = va

# data$parameter = c("Drift","Drift","Drift","Drift","Threshold","Threshold","Threshold","Threshold")

# Long to wide
data = pivot_wider(data = data, 
            id_cols = c(factor,fixed,isi), 
            names_from = parameter, 
            values_from = c("Mean","CI_lower","CI_upper"))

# data$factor = c("Speed", "Accuracy","Speed", "Accuracy")

data$factor = factor(data$factor, levels = c("Speed", "Accuracy"))
levels(data$factor) = c("Speed", "Accuracy")
data$isi = factor(data$isi, levels = c("ISI250", "ISI1000"))

levels(data$isi) = c("ISI250", "ISI1000")

# data$factor = c("Speed", "Accuracy","Speed & Accuracy" )

p<-ggplot(data,aes(x=Mean_Drift, y=Mean_Threshold,colour = factor,shape=fixed)) +
  geom_point(size=5) +
  geom_errorbar(width=0, size=1.1, position=position_dodge(width = .6),aes(xmin=CI_lower_Drift,xmax=CI_upper_Drift,linetype=fixed)) +
  geom_errorbar(width=0, size=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower_Threshold,ymax=CI_upper_Threshold,linetype=fixed))+
  facet_wrap(~isi)+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  ylab("Threshold") + 
  xlab("Drift Rate") + 
  scale_x_continuous(limits = c(2.2,3.4))+
  scale_y_continuous(limits = c(0.6,1.2))+
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none")  

p

```



## Stats

### Speed (drift) ISI=250


```{r, message=FALSE}

Speed_Goal = conditions_drift$Drift_Speed_Varying_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_V_250 = p


```

### Speed (drift) ISI=1000


```{r, message=FALSE}

Speed_Goal = conditions_drift$Drift_Speed_Varying_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_V_1000 = p


```

### Speed (threshold) ISI=250


```{r, message=FALSE}

Speed_Goal = conditions_threshold$Threshold_Speed_Varying_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_A_250 = p


```

### Speed (threshold) ISI=1000


```{r, message=FALSE}

Speed_Goal = conditions_threshold$Threshold_Speed_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_A_1000 = p


```


### Accuracy (drift) ISI=250


```{r, message=FALSE}

Accuracy_Goal = conditions_drift$Drift_Speed_Varying_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_V_250 = p


```

### Accuracy (drift) ISI=1000


```{r, message=FALSE}

Accuracy_Goal = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Accuracy_Fixed_ISI1000
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_V_1000 = p


```

### Accuracy (threshold) ISI=250


```{r, message=FALSE}

Accuracy_Goal = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Accuracy_Fixed_ISI250
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_A_250 = p


```

### Accuracy (threshold) ISI=1000


```{r, message=FALSE}

Accuracy_Goal = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Accuracy_Fixed_ISI1000
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_A_1000 = p


```



# Main analyses - Interval type x Block type on NDT


## Rhats

```{r, message=FALSE}
# Import the Rhats
rhats <- fread('output/Mixed/ae_only/modelMixed2/modelMixed2_RHat.csv', header = T)
colnames(rhats) = c("parameter","Rhat")


# Plot the Rhats

# Set parameters for plots
set_theme(base =theme_bw(base_size = 15, base_family = "")) # font size and theme
myColors = brewer.pal(3,"Set2") #colors
barfill <- "#4271AE"
barlines <- "#1F3552"

p =ggplot(rhats, aes(Rhat)) +
  geom_histogram(colour = barlines, fill = barfill,binwidth = 0.01)+ #colour = barlines, fill = barfill
  theme_bw() +
  labs(x = "Rhat", y = "Count\n")+
  theme(axis.line = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
        panel.grid.minor = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 18,  face = "bold",hjust = 0.5),
        text=element_text(colour="black", size = 14),
        axis.text.x=element_text(colour="black", size = 14),
        axis.text.y=element_text(colour="black", size = 14, face = "plain",hjust=0),
        axis.title=element_text(size=18,colour = "black",vjust = 1))

p


# Print the names of the low Rhat parameters
highRhats = subset(rhats,rhats$Rhat>1.1)
highRhats
```



## Trace plots


```{r, message=FALSE}
traces <- read.csv('output/Mixed/ae_only/modelMixed2/modelMixed2_traces.csv')

traces = traces %>% dplyr::select(v_Intercept,
                                 v_C.intervalType..Sum..S.Speed.,
                                 v_C.blockType..Sum..S.Varying.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 v_C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 
                                 a_Intercept,
                                 a_C.intervalType..Sum..S.Speed.,
                                 a_C.blockType..Sum..S.Varying.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 a_C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 
                                 t_Intercept,
                                 t_C.intervalType..Sum..S.Speed.,
                                 t_C.blockType..Sum..S.Varying.,
                                 t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 t_C.isi..Sum..S.ISI_250.,
                                 t_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 t_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)%>%
                          
            mutate(a_Intercept=0.5*a_Intercept,
                   a_C.intervalType..Sum..S.Speed.=0.5*a_C.intervalType..Sum..S.Speed.,
                   a_C.blockType..Sum..S.Varying.=0.5*a_C.blockType..Sum..S.Varying.,
                   a_C.isi..Sum..S.ISI_250.=0.5*a_C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                   a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                   a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)


# For each parameter
colNames= names(traces)

for (parameter in colNames) {

  #Plotting
  plot_data1 = traces[1:2000,]
  plot_data2 = traces[2001:4000,]
  plot_data3 = traces[4001:6000,]
  plot_data4 = traces[6001:8000,]
  plot_data5 = traces[8001:10000,]



  traces_plot = ggplot(NULL) +

    # Chain 1
    geom_line(data=plot_data1,mapping =aes_string(y=parameter,x = 1:2000), colour="red")+

    # Chain 2
    geom_line(data=plot_data2,mapping =aes_string(y=parameter,x = 1:2000), colour="royalblue1")+

    # Chain 3
    geom_line(data=plot_data3,mapping =aes_string(y=parameter,x = 1:2000), colour="springgreen")+

    # Chain 4
    geom_line(data=plot_data4,mapping =aes_string(y=parameter,x = 1:2000), colour="grey0")+

    # Chain 5
    geom_line(data=plot_data5,mapping =aes_string(y=parameter,x = 1:2000), colour="coral")+
    theme_classic(base_size = 18) +

    ggtitle(parameter)  + ylab("Parameter value") + xlab("Sample")



  print(traces_plot)
}
```




## PPCs


```{r, message=FALSE}

df.ppc <- fread('output/Mixed/ae_only/modelMixed2/modelMixed2_simData.csv') %>%
  mutate(simResponse=rt_sampled>0,
         Response=rt>0,
         rt_unsigned = abs(rt),
         rt_sampled_unsigned = abs(rt_sampled))


df.ppc.sim <- df.ppc %>% filter(sample==0,rt_sampled_unsigned<=3)

df.ppc.data <- df.ppc %>% filter(sample==0,rt_unsigned<=3)

ratio.true <- sum(!df.ppc.data$Response)/sum(df.ppc.data$Response)

ratio.simu <- sum(!df.ppc.sim$simResponse)/sum(df.ppc.sim$simResponse)

# Density plots with means
ggplot(df.ppc.data %>% filter(Response),
       aes(x=rt_unsigned,color='Correct',linetype='True')) +
  geom_density(size=1) +
  geom_density(data=df.ppc.data %>% filter(!Response),
               size=1,
               aes(x=rt_unsigned,y=-..density..*ratio.true,color='Incorrect',linetype='True'),
  ) +
  geom_density(data=df.ppc.sim %>% filter(simResponse),
               size=1,
               aes(x=rt_sampled_unsigned,color='Correct',linetype='Simulation')) +
  geom_density(data=df.ppc.sim %>% filter(!simResponse),
               size=1,
               aes(x=rt_sampled_unsigned,y=-..density..*ratio.simu,color='Incorrect',linetype='Simulation'),
  ) + geom_hline(yintercept=0) + ggdensity +
  xlab('Reaction Time') + coord_cartesian(xlim=c(0,2)) + facet_grid(cols=vars(intervalType,blockType,isi)) + scale_linetype_manual(name='Data:',values=c('Simulation'=1,'True'=2)) + scale_color_manual(name='Response:',values=c('Correct'='blue','Incorrect'='red'))
```





## Import the posteriors

### Transform the traces

```{r, message=FALSE}
traces = read.csv('output/Mixed/ae_only/modelMixed2/modelMixed2_traces.csv')


# Drift rates
traces_drift = traces %>% dplyr::select(v_Intercept,
                                 v_C.intervalType..Sum..S.Speed.,
                                 v_C.blockType..Sum..S.Varying.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 v_C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)

traces.mat = t(data.matrix(traces_drift))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_drift = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_drift) = c("Drift_Speed_Varying_ISI250",
                           "Drift_Accuracy_Varying_ISI250",
                           "Drift_Speed_Fixed_ISI250",
                           "Drift_Accuracy_Fixed_ISI250",
                           "Drift_Speed_Varying_ISI1000",
                           "Drift_Accuracy_Varying_ISI1000",
                           "Drift_Speed_Fixed_ISI1000",
                           "Drift_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_drift$Drift_Varying_ISI250 = conditions_drift$Drift_Accuracy_Varying_ISI250 - conditions_drift$Drift_Speed_Varying_ISI250
conditions_drift$Drift_Varying_ISI1000 = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Speed_Varying_ISI1000

conditions_drift$Drift_Fixed_ISI250 = conditions_drift$Drift_Accuracy_Fixed_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
conditions_drift$Drift_Fixed_ISI1000 = conditions_drift$Drift_Accuracy_Fixed_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000




# Thresholds
traces_threshold = traces %>% dplyr::select(a_Intercept,
                                 a_C.intervalType..Sum..S.Speed.,
                                 a_C.blockType..Sum..S.Varying.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 a_C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)%>%
                          
            mutate(a_Intercept=0.5*a_Intercept,
                   a_C.intervalType..Sum..S.Speed.=0.5*a_C.intervalType..Sum..S.Speed.,
                   a_C.blockType..Sum..S.Varying.=0.5*a_C.blockType..Sum..S.Varying.,
                   a_C.isi..Sum..S.ISI_250.=0.5*a_C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                   a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                   a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)


traces.mat = t(data.matrix(traces_threshold))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_threshold = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_threshold) = c("Threshold_Speed_Varying_ISI250",
                           "Threshold_Accuracy_Varying_ISI250",
                           "Threshold_Speed_Fixed_ISI250",
                           "Threshold_Accuracy_Fixed_ISI250",
                           "Threshold_Speed_Varying_ISI1000",
                           "Threshold_Accuracy_Varying_ISI1000",
                           "Threshold_Speed_Fixed_ISI1000",
                           "Threshold_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_threshold$Threshold_Varying_ISI250 = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Speed_Varying_ISI250
conditions_threshold$Threshold_Varying_ISI1000 = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Varying_ISI1000

conditions_threshold$Threshold_Fixed_ISI250 = conditions_threshold$Threshold_Accuracy_Fixed_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
conditions_threshold$Threshold_Fixed_ISI1000 = conditions_threshold$Threshold_Accuracy_Fixed_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000


# NDT
traces_ndt = traces %>% dplyr::select(t_Intercept,
                                 t_C.intervalType..Sum..S.Speed.,
                                 t_C.blockType..Sum..S.Varying.,
                                 t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 t_C.isi..Sum..S.ISI_250.,
                                 t_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 t_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)

traces.mat = t(data.matrix(traces_ndt))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_ndt = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_ndt) = c("NDT_Speed_Varying_ISI250",
                           "NDT_Accuracy_Varying_ISI250",
                           "NDT_Speed_Fixed_ISI250",
                           "NDT_Accuracy_Fixed_ISI250",
                           "NDT_Speed_Varying_ISI1000",
                           "NDT_Accuracy_Varying_ISI1000",
                           "NDT_Speed_Fixed_ISI1000",
                           "NDT_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_ndt$NDT_Varying_ISI250 = conditions_ndt$NDT_Accuracy_Varying_ISI250 - conditions_ndt$NDT_Speed_Varying_ISI250
conditions_ndt$NDT_Varying_ISI1000 = conditions_ndt$NDT_Accuracy_Varying_ISI1000 - conditions_ndt$NDT_Speed_Varying_ISI1000

conditions_ndt$NDT_Fixed_ISI250 = conditions_ndt$NDT_Accuracy_Fixed_ISI250 - conditions_ndt$NDT_Speed_Fixed_ISI250
conditions_ndt$NDT_Fixed_ISI1000 = conditions_ndt$NDT_Accuracy_Fixed_ISI1000 - conditions_ndt$NDT_Speed_Fixed_ISI1000

# Take only the difference variables
# conditions_threshold = conditions_threshold[,9:12]

# First column of condition.mu will be  1 1 1 which means all high, which means Speed, Varying, and ISI_250
# Second column will be -1 1 1 which means Accuracy, Varying, ISI_250

# f,  g,  h
# 1,  1,  1
#-1,  1,  1
# 1, -1,  1
#-1, -1,  1
# 1,  1, -1
#-1,  1, -1
# 1, -1, -1
#-1, -1, -1


  


```

### Summarry of the parameter estimates

```{r, message=FALSE}

# Drift - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_drift$v_C.intervalType..Sum..S.Speed. = traces_drift$v_C.intervalType..Sum..S.Speed.*2
traces_drift$v_C.blockType..Sum..S.Varying. = traces_drift$v_C.blockType..Sum..S.Varying.*2
traces_drift$v_C.isi..Sum..S.ISI_250. = traces_drift$v_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_drift$v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_drift$v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_drift$v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_drift$v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
drift.rate = test.params(traces_drift)

# Print the summary
kable(drift.rate,caption="Drift rate parameter estimates")

# Threshold - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_threshold$a_C.intervalType..Sum..S.Speed. = traces_threshold$a_C.intervalType..Sum..S.Speed.*2
traces_threshold$a_C.blockType..Sum..S.Varying. = traces_threshold$a_C.blockType..Sum..S.Varying.*2
traces_threshold$a_C.isi..Sum..S.ISI_250. = traces_threshold$a_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_threshold$a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_threshold$a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
threshold = test.params(traces_threshold)

# Print the summary
kable(threshold,caption="Threshold parameter estimates")

# NDT - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_ndt$t_C.intervalType..Sum..S.Speed. = traces_ndt$t_C.intervalType..Sum..S.Speed.*2
traces_ndt$t_C.blockType..Sum..S.Varying. = traces_ndt$t_C.blockType..Sum..S.Varying.*2
traces_ndt$t_C.isi..Sum..S.ISI_250. = traces_ndt$t_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_ndt$t_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_ndt$t_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_ndt$t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_ndt$t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_ndt$t_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_ndt$t_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_ndt$t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_ndt$t_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
ndt = test.params(traces_threshold)

# Print the summary
kable(ndt,caption="NDT parameter estimates")


```

### Summarize the posteriors

```{r, message=FALSE}

drift.rate <- test.params(conditions_drift)
# Take only the difference variables
drift.rate = drift.rate[9:12,]

threshold <- test.params(conditions_threshold)
# Take only the difference variables
threshold = threshold[9:12,]

ndt <- test.params(conditions_ndt)
# Take only the difference variables
ndt = ndt[9:12,]

va <- rbind(drift.rate,threshold) %>% separate(parameter,c('parameter','fixed','isi'),'_')
va = as.data.frame(va)
va$parameter = as.factor(va$parameter)
va$fixed = as.factor(va$fixed)
va$isi = as.factor(va$isi)
va$isi = ifelse(va$isi=="ISI250", "250", "1000")
va$isi = factor(va$isi,levels=c("250","1000"))

ndt <- ndt %>% separate(parameter,c('parameter','fixed','isi'),'_')
ndt = as.data.frame(ndt)
ndt$parameter = as.factor(ndt$parameter)
ndt$fixed = as.factor(ndt$fixed)
ndt$isi = as.factor(ndt$isi)
ndt$isi = ifelse(ndt$isi=="ISI250", "250", "1000")
ndt$isi = factor(ndt$isi,levels=c("250","1000"))


```


## Drift rate and threshold

### Bar plot

```{r, message=FALSE}



# Plot
p<-ggplot(va,aes(x=isi, y=Mean,fill=fixed)) +
  geom_bar(width=0.6,stat="identity", position=position_dodge(0.6)) +
  geom_errorbar(width=.1, size=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower,ymax=CI_upper)) + ylab('Estimate') +
  facet_wrap(vars(parameter), labeller = as_labeller(c('Drift'="Drift rate",'Threshold'="Threshold")))+
  ylim(-0.1,0.4)+
  # labs(x="SOA (ms)")+
  geom_hline(yintercept=0) +
  scale_fill_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  scale_x_discrete(expand = c(0.3,0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0)),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.title.x=element_blank(),
        # axis.text.x = element_text(color="black"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.85, 0.90),
        legend.background = element_rect(fill = "transparent", color = NA))  
        
p



# ggsave("Mixed_ae_only_VAT.tiff", units="in", width=15, height=4, dpi=400, compression = 'lzw')
kable(va)

# Conditions of interest

# Threshold
threshold_Fixed_min_Varying_isi250 = conditions_threshold$Threshold_Fixed_ISI250 - conditions_threshold$Threshold_Varying_ISI250
threshold_Fixed_min_Varying_isi1000 = conditions_threshold$Threshold_Fixed_ISI1000 - conditions_threshold$Threshold_Varying_ISI1000
threshold_Fixed_min_Varying = (threshold_Fixed_min_Varying_isi250 + threshold_Fixed_min_Varying_isi1000)/2
threshold_Acc_min_Speed = (conditions_threshold$Threshold_Fixed_ISI250+
                           conditions_threshold$Threshold_Varying_ISI250+
                           conditions_threshold$Threshold_Fixed_ISI1000+
                           conditions_threshold$Threshold_Varying_ISI1000)/4

#Drift
drift_Fixed_min_Varying_isi250 = conditions_drift$Drift_Fixed_ISI250 - conditions_drift$Drift_Varying_ISI250
drift_Fixed_min_Varying_isi1000 = conditions_drift$Drift_Fixed_ISI1000 - conditions_drift$Drift_Varying_ISI1000
drift_Fixed_min_Varying = (drift_Fixed_min_Varying_isi250 + drift_Fixed_min_Varying_isi1000)/2
drift_Acc_min_Speed = (conditions_drift$Drift_Fixed_ISI250+
                       conditions_drift$Drift_Varying_ISI250+
                       conditions_drift$Drift_Fixed_ISI1000+
                       conditions_drift$Drift_Varying_ISI1000)/4


# Main effects
#---------------------------------------------------------------------------------------
# Threshold - main effect of the condition type
table = test.params(as.data.frame(threshold_Acc_min_Speed))
table[1] = "Threshold (Acc-Speed)"
kable(table)

# Drift - main effect of the condition type
table = test.params(as.data.frame(drift_Acc_min_Speed))
table[1] = "Drift (Acc-Speed)"
kable(table)


# Threshold - Block x condition
table = test.params(as.data.frame(threshold_Fixed_min_Varying))
table[1] = "Threshold (Fixed-Varying) X (Acc-Speed)"
kable(table)

# Drift - Block x condition
table = test.params(as.data.frame(drift_Fixed_min_Varying))
table[1] = "Drift (Fixed-Varying) X (Acc-Speed)"
kable(table)

# Fixed vs. varying
#---------------------------------------------------------------------------------------

# # Threshold - difference between fixed and varying ISI 250
# summarize_posterior(threshold_Fixed_min_Varying_isi250, rep(0,length(threshold_Fixed_min_Varying_isi250)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250))
# table[1] = "Threshold (Fixed-Varying) ISI250"
# kable(table)
# 
# # Threshold - difference between fixed and varying ISI 1000
# summarize_posterior(threshold_Fixed_min_Varying_isi1000, rep(0,length(threshold_Fixed_min_Varying_isi1000)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi1000))
# table[1] = "Threshold (Fixed-Varying) ISI1000"
# kable(table)

# Threshold - difference between 250 and 1000
#summarize_posterior(threshold_Fixed_min_Varying_isi250, threshold_Fixed_min_Varying_isi1000, "Threshold: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250 - threshold_Fixed_min_Varying_isi1000))
table[1] = "Threshold: 3-way interaction"
kable(table)

# # Drift - difference between fixed and varying ISI 250
# summarize_posterior(drift_Fixed_min_Varying_isi250, rep(0,length(drift_Fixed_min_Varying_isi250)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250))
# table[1] = "Drift (Fixed-Varying) ISI250"
# kable(table)
# 
# # Drift - difference between fixed and varying ISI 1000
# summarize_posterior(drift_Fixed_min_Varying_isi1000, rep(0,length(drift_Fixed_min_Varying_isi1000)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi1000))
# table[1] = "Drift (Fixed-Varying) ISI1000"
# kable(table)

# Drift - difference between 250 and 1000
#summarize_posterior(drift_Fixed_min_Varying_isi250, drift_Fixed_min_Varying_isi1000, "drift: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250 - drift_Fixed_min_Varying_isi1000))
table[1] = "Drift: 3-way interaction"
kable(table)


# # Save the figure
# pdf(file="../../../Manuscript/figures/Figure_Exp6_DDM.pdf",height=4,width=8)
# 
# p = cowplot::plot_grid(Exp6.DDM,
#                        nrow = 1)
# p
# dev.off()

```


### Points in 2D 

```{r, message=FALSE}


drift.rate<- test.params(conditions_drift)[1:8,]

threshold<- test.params(conditions_threshold)[1:8,]


va <- rbind(drift.rate,threshold) %>% separate(parameter,c('parameter','factor','fixed','isi'),'_')

va$factor = as.factor(va$factor)

# va$parameter<-factor(va$parameter,labels=c('Threshold','Drift Rate'))


# data = subset(va,fixed=="Varying")
# data = subset(va,isi=="ISI250")

data = va

# data$parameter = c("Drift","Drift","Drift","Drift","Threshold","Threshold","Threshold","Threshold")

# Long to wide
data = pivot_wider(data = data, 
            id_cols = c(factor,fixed,isi), 
            names_from = parameter, 
            values_from = c("Mean","CI_lower","CI_upper"))

# data$factor = c("Speed", "Accuracy","Speed", "Accuracy")

data$factor = factor(data$factor, levels = c("Speed", "Accuracy"))
levels(data$factor) = c("Speed", "Accuracy")
data$isi = factor(data$isi, levels = c("ISI250", "ISI1000"))

levels(data$isi) = c("ISI250", "ISI1000")

# data$factor = c("Speed", "Accuracy","Speed & Accuracy" )

p<-ggplot(data,aes(x=Mean_Drift, y=Mean_Threshold,colour = factor,shape=fixed)) +
  geom_point(size=5) +
  geom_errorbar(width=0, size=1.1, position=position_dodge(width = .6),aes(xmin=CI_lower_Drift,xmax=CI_upper_Drift,linetype=fixed)) +
  geom_errorbar(width=0, size=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower_Threshold,ymax=CI_upper_Threshold,linetype=fixed))+
  facet_wrap(~isi)+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  ylab("Threshold") + 
  xlab("Drift Rate") + 
  scale_x_continuous(limits = c(2.2,3.4))+
  scale_y_continuous(limits = c(0.6,1.2))+
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none")  

p




```




## NDT

### Bar plot

```{r, message=FALSE}


# Plot
p<-ggplot(ndt,aes(x=isi, y=Mean,fill=fixed)) +
  geom_bar(width=0.6,stat="identity", position=position_dodge(0.6)) +
  geom_errorbar(width=.1, size=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower,ymax=CI_upper)) + ylab('Estimate') +
  facet_wrap(vars(parameter), labeller = as_labeller(c('Drift'="Drift rate",'Threshold'="Threshold")))+
  ylim(-0.1,0.4)+
  # labs(x="SOA (ms)")+
  geom_hline(yintercept=0) +
  scale_fill_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  scale_x_discrete(expand = c(0.3,0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0)),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.title.x=element_blank(),
        # axis.text.x = element_text(color="black"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.85, 0.90),
        legend.background = element_rect(fill = "transparent", color = NA))  
        
p

# Exp6.DDM = p


# ggsave("Mixed_ae_only_VAT.tiff", units="in", width=15, height=4, dpi=400, compression = 'lzw')
kable(ndt)

# Conditions of interest

#NDT
ndt_Fixed_min_Varying_isi250 = conditions_ndt$NDT_Fixed_ISI250 - conditions_ndt$NDT_Varying_ISI250
ndt_Fixed_min_Varying_isi1000 = conditions_ndt$NDT_Fixed_ISI1000 - conditions_ndt$NDT_Varying_ISI1000
ndt_Fixed_min_Varying = (ndt_Fixed_min_Varying_isi250 + ndt_Fixed_min_Varying_isi1000)/2
ndt_Acc_min_Speed = (conditions_ndt$NDT_Fixed_ISI250+
                       conditions_ndt$NDT_Varying_ISI250+
                       conditions_ndt$NDT_Fixed_ISI1000+
                       conditions_ndt$NDTt_Varying_ISI1000)/4


# Main effects
#---------------------------------------------------------------------------------------
# NDT - main effect of the condition type
table = test.params(as.data.frame(ndt_Acc_min_Speed))
table[1] = "NDT (Acc-Speed)"
kable(table)


# NDT - Block x condition
table = test.params(as.data.frame(ndt_Fixed_min_Varying))
table[1] = "NDT (Fixed-Varying) X (Acc-Speed)"
kable(table)



# Fixed vs. varying
#---------------------------------------------------------------------------------------

# # Threshold - difference between fixed and varying ISI 250
# summarize_posterior(threshold_Fixed_min_Varying_isi250, rep(0,length(threshold_Fixed_min_Varying_isi250)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250))
# table[1] = "Threshold (Fixed-Varying) ISI250"
# kable(table)
# 
# # Threshold - difference between fixed and varying ISI 1000
# summarize_posterior(threshold_Fixed_min_Varying_isi1000, rep(0,length(threshold_Fixed_min_Varying_isi1000)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi1000))
# table[1] = "Threshold (Fixed-Varying) ISI1000"
# kable(table)

# Threshold - difference between 250 and 1000
#summarize_posterior(threshold_Fixed_min_Varying_isi250, threshold_Fixed_min_Varying_isi1000, "Threshold: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(ndt_Fixed_min_Varying_isi250 - ndt_Fixed_min_Varying_isi1000))
table[1] = "NDT: 3-way interaction"
kable(table)

# # Drift - difference between fixed and varying ISI 250
# summarize_posterior(drift_Fixed_min_Varying_isi250, rep(0,length(drift_Fixed_min_Varying_isi250)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250))
# table[1] = "Drift (Fixed-Varying) ISI250"
# kable(table)
# 
# # Drift - difference between fixed and varying ISI 1000
# summarize_posterior(drift_Fixed_min_Varying_isi1000, rep(0,length(drift_Fixed_min_Varying_isi1000)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi1000))
# table[1] = "Drift (Fixed-Varying) ISI1000"
# kable(table)


# # Save the figure
# pdf(file="../../../Manuscript/figures/Figure_Exp6_DDM.pdf",height=4,width=8)
# 
# p = cowplot::plot_grid(Exp6.DDM,
#                        nrow = 1)
# p
# dev.off()

```






## Stats

### Speed (drift) ISI=250


```{r, message=FALSE}

Speed_Goal = conditions_drift$Drift_Speed_Varying_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_V_250 = p


```

### Speed (drift) ISI=1000


```{r, message=FALSE}

Speed_Goal = conditions_drift$Drift_Speed_Varying_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_V_1000 = p


```

### Speed (threshold) ISI=250


```{r, message=FALSE}

Speed_Goal = conditions_threshold$Threshold_Speed_Varying_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_A_250 = p


```

### Speed (threshold) ISI=1000


```{r, message=FALSE}

Speed_Goal = conditions_threshold$Threshold_Speed_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_A_1000 = p


```


### Accuracy (drift) ISI=250


```{r, message=FALSE}

Accuracy_Goal = conditions_drift$Drift_Speed_Varying_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_V_250 = p


```

### Accuracy (drift) ISI=1000


```{r, message=FALSE}

Accuracy_Goal = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Accuracy_Fixed_ISI1000
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_V_1000 = p


```

### Accuracy (threshold) ISI=250


```{r, message=FALSE}

Accuracy_Goal = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Accuracy_Fixed_ISI250
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_A_250 = p


```

### Accuracy (threshold) ISI=1000


```{r, message=FALSE}

Accuracy_Goal = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Accuracy_Fixed_ISI1000
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_A_1000 = p


```


## Non-decision time


```{r, message=FALSE}

# # NDT
# NDT <- NDT %>% separate(parameter,c('parameter','factor'),'_')
# 
# labels <- c('NDT')
# 
# NDT$factor = as.factor(NDT$factor)
# 
# NDT$parameter<-factor(NDT$parameter,labels=c('NDT'))
# 
# # Plot
# PlotNDT<-ggplot(NDT,aes(x=parameter, y=Mean,fill=factor)) +
#   geom_bar(stat="identity", position=position_dodge(width = 0.5),width=0.5) +
#   geom_errorbar(width=.1, size=1, position=position_dodge(width = .5),aes(ymin=CI_lower,ymax=CI_upper)) + ylab('Estimate') +
#   ggtitle('NDT')+
#   # ylim(-0.2,0.5)+
#   theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,15,5,5), "mm"),
#         axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
#         text = element_text(size=20),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.border = element_blank(),
#         panel.background = element_blank(),
#         axis.title.x=element_blank(),
#         plot.title = element_text(hjust = 0.5,size = 20, face = "bold")) + geom_hline(yintercept=0) +
#   scale_x_discrete(labels= labels) +
#         scale_fill_manual(name="",values=c(rgb(0.6, 0.6, 0.6),rgb(0.8, 0.8, 0.8),rgb(0.7, 0.7, 0.7)))
# PlotNDT
# 
# kable(NDT)
# 
# # Differences Acc-Speed
# summarize_posterior(traces$t_Acc, traces$t_Speed, "NDT (Speed - Accuracy)")
# table = test.params(as.data.frame(traces$t_Acc - traces$t_Speed))
# table[1] = "NDT (Speed - Accuracy)"
# kable(table)

```










# Main analyses - Intercept on NDT


## Rhats

```{r, message=FALSE}
# Import the Rhats
rhats <- fread('output/Mixed/ae_only/modelMixed3/modelMixed3_RHat.csv', header = T)
colnames(rhats) = c("parameter","Rhat")


# Plot the Rhats

# Set parameters for plots
set_theme(base =theme_bw(base_size = 15, base_family = "")) # font size and theme
myColors = brewer.pal(3,"Set2") #colors
barfill <- "#4271AE"
barlines <- "#1F3552"

p =ggplot(rhats, aes(Rhat)) +
  geom_histogram(colour = barlines, fill = barfill,binwidth = 0.01)+ #colour = barlines, fill = barfill
  theme_bw() +
  labs(x = "Rhat", y = "Count\n")+
  theme(axis.line = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
        panel.grid.minor = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 18,  face = "bold",hjust = 0.5),
        text=element_text(colour="black", size = 14),
        axis.text.x=element_text(colour="black", size = 14),
        axis.text.y=element_text(colour="black", size = 14, face = "plain",hjust=0),
        axis.title=element_text(size=18,colour = "black",vjust = 1))

p


# Print the names of the low Rhat parameters
highRhats = subset(rhats,rhats$Rhat>1.1)
highRhats
```



## Trace plots


```{r, message=FALSE}
traces <- read.csv('output/Mixed/ae_only/modelMixed3/modelMixed3_traces.csv')

traces = traces %>% dplyr::select(v_Intercept,
                                 v_C.intervalType..Sum..S.Speed.,
                                 v_C.blockType..Sum..S.Varying.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 v_C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_Intercept,
                                 a_C.intervalType..Sum..S.Speed.,
                                 a_C.blockType..Sum..S.Varying.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 a_C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 t)%>%
                          
            mutate(a_Intercept=0.5*a_Intercept,
                   a_C.intervalType..Sum..S.Speed.=0.5*a_C.intervalType..Sum..S.Speed.,
                   a_C.blockType..Sum..S.Varying.=0.5*a_C.blockType..Sum..S.Varying.,
                   a_C.isi..Sum..S.ISI_250.=0.5*a_C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                   a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                   a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)


# For each parameter
colNames= names(traces)

for (parameter in colNames) {

  #Plotting
  plot_data1 = traces[1:2000,]
  plot_data2 = traces[2001:4000,]
  plot_data3 = traces[4001:6000,]
  plot_data4 = traces[6001:8000,]
  plot_data5 = traces[8001:10000,]



  traces_plot = ggplot(NULL) +

    # Chain 1
    geom_line(data=plot_data1,mapping =aes_string(y=parameter,x = 1:2000), colour="red")+

    # Chain 2
    geom_line(data=plot_data2,mapping =aes_string(y=parameter,x = 1:2000), colour="royalblue1")+

    # Chain 3
    geom_line(data=plot_data3,mapping =aes_string(y=parameter,x = 1:2000), colour="springgreen")+

    # Chain 4
    geom_line(data=plot_data4,mapping =aes_string(y=parameter,x = 1:2000), colour="grey0")+

    # Chain 5
    geom_line(data=plot_data5,mapping =aes_string(y=parameter,x = 1:2000), colour="coral")+
    theme_classic(base_size = 18) +

    ggtitle(parameter)  + ylab("Parameter value") + xlab("Sample")



  print(traces_plot)
}
```




## PPCs


```{r, message=FALSE}

df.ppc <- fread('output/Mixed/ae_only/modelMixed3/modelMixed3_simData.csv') %>%
  mutate(simResponse=rt_sampled>0,
         Response=rt>0,
         rt_unsigned = abs(rt),
         rt_sampled_unsigned = abs(rt_sampled))


df.ppc.sim <- df.ppc %>% filter(sample==0,rt_sampled_unsigned<=3)

df.ppc.data <- df.ppc %>% filter(sample==0,rt_unsigned<=3)

ratio.true <- sum(!df.ppc.data$Response)/sum(df.ppc.data$Response)

ratio.simu <- sum(!df.ppc.sim$simResponse)/sum(df.ppc.sim$simResponse)

# Density plots with means
ggplot(df.ppc.data %>% filter(Response),
       aes(x=rt_unsigned,color='Correct',linetype='True')) +
  geom_density(size=1) +
  geom_density(data=df.ppc.data %>% filter(!Response),
               size=1,
               aes(x=rt_unsigned,y=-..density..*ratio.true,color='Incorrect',linetype='True'),
  ) +
  geom_density(data=df.ppc.sim %>% filter(simResponse),
               size=1,
               aes(x=rt_sampled_unsigned,color='Correct',linetype='Simulation')) +
  geom_density(data=df.ppc.sim %>% filter(!simResponse),
               size=1,
               aes(x=rt_sampled_unsigned,y=-..density..*ratio.simu,color='Incorrect',linetype='Simulation'),
  ) + geom_hline(yintercept=0) + ggdensity +
  xlab('Reaction Time') + coord_cartesian(xlim=c(0,2)) + facet_grid(cols=vars(intervalType,blockType,isi)) + scale_linetype_manual(name='Data:',values=c('Simulation'=1,'True'=2)) + scale_color_manual(name='Response:',values=c('Correct'='blue','Incorrect'='red'))
```





## Import the posteriors

### Transform the traces

```{r, message=FALSE}

# traces<-traces %>% dplyr::select(t,
#                                  z_C.congruency..Sum..S.incongruent.,
#                                  p_outlier)
# 
# summary = test.params(traces)
# 
traces = read.csv('output/Mixed/ae_only/modelMixed3/modelMixed3_traces.csv')


# Drift rates
traces_drift = traces %>% dplyr::select(v_Intercept,
                                 v_C.intervalType..Sum..S.Speed.,
                                 v_C.blockType..Sum..S.Varying.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 v_C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)

traces_drift$v_Intercept = rep(mean(traces_drift$v_Intercept), length(traces_drift$v_Intercept))


traces.mat = t(data.matrix(traces_drift))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_drift = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_drift) = c("Drift_Speed_Varying_ISI250",
                           "Drift_Accuracy_Varying_ISI250",
                           "Drift_Speed_Fixed_ISI250",
                           "Drift_Accuracy_Fixed_ISI250",
                           "Drift_Speed_Varying_ISI1000",
                           "Drift_Accuracy_Varying_ISI1000",
                           "Drift_Speed_Fixed_ISI1000",
                           "Drift_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_drift$Drift_Varying_ISI250 = conditions_drift$Drift_Accuracy_Varying_ISI250 - conditions_drift$Drift_Speed_Varying_ISI250
conditions_drift$Drift_Varying_ISI1000 = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Speed_Varying_ISI1000

conditions_drift$Drift_Fixed_ISI250 = conditions_drift$Drift_Accuracy_Fixed_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
conditions_drift$Drift_Fixed_ISI1000 = conditions_drift$Drift_Accuracy_Fixed_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000




# Thresholds
traces_threshold = traces %>% dplyr::select(a_Intercept,
                                 a_C.intervalType..Sum..S.Speed.,
                                 a_C.blockType..Sum..S.Varying.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                                 a_C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                                 a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                                 a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)%>%
                          
            mutate(a_Intercept=0.5*a_Intercept,
                   a_C.intervalType..Sum..S.Speed.=0.5*a_C.intervalType..Sum..S.Speed.,
                   a_C.blockType..Sum..S.Varying.=0.5*a_C.blockType..Sum..S.Varying.,
                   a_C.isi..Sum..S.ISI_250.=0.5*a_C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.,
                   a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.,
                   a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.,
                   a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.=0.5*a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.)
traces_threshold$a_Intercept = rep(mean(traces_threshold$a_Intercept), length(traces_threshold$a_Intercept))


traces.mat = t(data.matrix(traces_threshold))


coding.intervalType = cbind(c(1,1),contr.sum(2))
coding.blockType = cbind(c(1,1),contr.sum(2))
coding.isi = cbind(c(1,1),contr.sum(2))
coding.total = coding.isi %x% coding.blockType %x% coding.intervalType

conditions_threshold = as.data.frame(t(coding.total %*% traces.mat))

colnames(conditions_threshold) = c("Threshold_Speed_Varying_ISI250",
                           "Threshold_Accuracy_Varying_ISI250",
                           "Threshold_Speed_Fixed_ISI250",
                           "Threshold_Accuracy_Fixed_ISI250",
                           "Threshold_Speed_Varying_ISI1000",
                           "Threshold_Accuracy_Varying_ISI1000",
                           "Threshold_Speed_Fixed_ISI1000",
                           "Threshold_Accuracy_Fixed_ISI1000")

# Calculate the difference
conditions_threshold$Threshold_Varying_ISI250 = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Speed_Varying_ISI250
conditions_threshold$Threshold_Varying_ISI1000 = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Varying_ISI1000

conditions_threshold$Threshold_Fixed_ISI250 = conditions_threshold$Threshold_Accuracy_Fixed_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
conditions_threshold$Threshold_Fixed_ISI1000 = conditions_threshold$Threshold_Accuracy_Fixed_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000

# Take only the difference variables
# conditions_threshold = conditions_threshold[,9:12]

# First column of condition.mu will be  1 1 1 which means all high, which means Speed, Varying, and ISI_250
# Second column will be -1 1 1 which means Accuracy, Varying, ISI_250

# f,  g,  h
# 1,  1,  1
#-1,  1,  1
# 1, -1,  1
#-1, -1,  1
# 1,  1, -1
#-1,  1, -1
# 1, -1, -1
#-1, -1, -1


  


```

### Summarry of the parameter estimates

```{r, message=FALSE}
print("NDT mean")
mean(traces$t)

# Drift - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_drift$v_C.intervalType..Sum..S.Speed. = traces_drift$v_C.intervalType..Sum..S.Speed.*2
traces_drift$v_C.blockType..Sum..S.Varying. = traces_drift$v_C.blockType..Sum..S.Varying.*2
traces_drift$v_C.isi..Sum..S.ISI_250. = traces_drift$v_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_drift$v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_drift$v_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_drift$v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_drift$v_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_drift$v_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
drift.rate = test.params(traces_drift)

# Print the summary
kable(drift.rate,caption="Drift rate parameter estimates")

# Threshold - summarize and multiply to get the correct values (due to sum coding, we multiply by 2 each of the estimates)
# Main effects
traces_threshold$a_C.intervalType..Sum..S.Speed. = traces_threshold$a_C.intervalType..Sum..S.Speed.*2
traces_threshold$a_C.blockType..Sum..S.Varying. = traces_threshold$a_C.blockType..Sum..S.Varying.*2
traces_threshold$a_C.isi..Sum..S.ISI_250. = traces_threshold$a_C.isi..Sum..S.ISI_250.*2

# 2-way interactions
traces_threshold$a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. * 4
traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying.*4
traces_threshold$a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.isi..Sum..S.ISI_250.*4

# 3-way interaction
traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250. = traces_threshold$a_C.intervalType..Sum..S.Speed..C.blockType..Sum..S.Varying..C.isi..Sum..S.ISI_250.*8

# Summarize
threshold = test.params(traces_threshold)

# Print the summary
kable(threshold,caption="Threshold parameter estimates")


summary <- threshold
summary$CI_upper <- round(summary$CI_upper,2)
summary$CI_lower <- round(summary$CI_lower,2)
summary$CI <- paste0(summary$CI_lower,", ",summary$CI_upper)
summary$Mean <- round(summary$Mean,2)
summary$pvalue <- round(summary$pvalue,2)


kable(summary)

```

### Summarize the posteriors

```{r, message=FALSE}

drift.rate <- test.params(conditions_drift)
# Take only the difference variables
drift.rate = drift.rate[9:12,]

threshold <- test.params(conditions_threshold)
# Take only the difference variables
threshold = threshold[9:12,]

# NDT<- output %>% filter(parameter %in% c('t_Speed',
#                                          't_Acc'))

va <- rbind(drift.rate,threshold) %>% separate(parameter,c('parameter','fixed','isi'),'_')
va = as.data.frame(va)
va$parameter = as.factor(va$parameter)
va$fixed = as.factor(va$fixed)
va$isi = as.factor(va$isi)
va$isi = ifelse(va$isi=="ISI250", "250", "1000")
va$isi = factor(va$isi,levels=c("250","1000"))


```


## Drift rate and threshold

### Bar plot

```{r, message=FALSE}



# Plot
p<-ggplot(va,aes(x=isi, y=Mean,fill=fixed)) +
  geom_bar(width=0.6,stat="identity", position=position_dodge(0.6)) +
  geom_errorbar(width=.1, size=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower,ymax=CI_upper)) + ylab('Estimate') +
  facet_wrap(vars(parameter), labeller = as_labeller(c('Drift'="Drift rate",'Threshold'="Threshold")))+
  ylim(-0.1,0.4)+
  # labs(x="SOA (ms)")+
  geom_hline(yintercept=0) +
  scale_fill_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  scale_x_discrete(expand = c(0.3,0.3))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0)),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.title.x=element_blank(),
        # axis.text.x = element_text(color="black"),
        axis.text.x = element_blank(),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.85, 0.90),
        legend.background = element_rect(fill = "transparent", color = NA))  
        
p



# ggsave("Mixed_ae_only_VAT.tiff", units="in", width=15, height=4, dpi=400, compression = 'lzw')
kable(va)



# Threshold
threshold_Fixed_min_Varying_isi250 = conditions_threshold$Threshold_Fixed_ISI250 - conditions_threshold$Threshold_Varying_ISI250
threshold_Fixed_min_Varying_isi1000 = conditions_threshold$Threshold_Fixed_ISI1000 - conditions_threshold$Threshold_Varying_ISI1000
threshold_Fixed_min_Varying = (threshold_Fixed_min_Varying_isi250 + threshold_Fixed_min_Varying_isi1000)/2
threshold_Acc_min_Speed = (conditions_threshold$Threshold_Fixed_ISI250+
                           conditions_threshold$Threshold_Varying_ISI250+
                           conditions_threshold$Threshold_Fixed_ISI1000+
                           conditions_threshold$Threshold_Varying_ISI1000)/4

#Drift
drift_Fixed_min_Varying_isi250 = conditions_drift$Drift_Fixed_ISI250 - conditions_drift$Drift_Varying_ISI250
drift_Fixed_min_Varying_isi1000 = conditions_drift$Drift_Fixed_ISI1000 - conditions_drift$Drift_Varying_ISI1000
drift_Fixed_min_Varying = (drift_Fixed_min_Varying_isi250 + drift_Fixed_min_Varying_isi1000)/2
drift_Acc_min_Speed = (conditions_drift$Drift_Fixed_ISI250+
                       conditions_drift$Drift_Varying_ISI250+
                       conditions_drift$Drift_Fixed_ISI1000+
                       conditions_drift$Drift_Varying_ISI1000)/4


# Main effects
#---------------------------------------------------------------------------------------
# Threshold - main effect of the condition type
table = test.params(as.data.frame(threshold_Acc_min_Speed))
table[1] = "Threshold (Acc-Speed)"
kable(table)

# Drift - main effect of the condition type
table = test.params(as.data.frame(drift_Acc_min_Speed))
table[1] = "Drift (Acc-Speed)"
kable(table)


# Threshold - Block x condition
table = test.params(as.data.frame(threshold_Fixed_min_Varying))
table[1] = "Threshold (Fixed-Varying) X (Acc-Speed)"
kable(table)

# Drift - Block x condition
table = test.params(as.data.frame(drift_Fixed_min_Varying))
table[1] = "Drift (Fixed-Varying) X (Acc-Speed)"
kable(table)

# Fixed vs. varying
#---------------------------------------------------------------------------------------

# # Threshold - difference between fixed and varying ISI 250
# summarize_posterior(threshold_Fixed_min_Varying_isi250, rep(0,length(threshold_Fixed_min_Varying_isi250)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250))
# table[1] = "Threshold (Fixed-Varying) ISI250"
# kable(table)
# 
# # Threshold - difference between fixed and varying ISI 1000
# summarize_posterior(threshold_Fixed_min_Varying_isi1000, rep(0,length(threshold_Fixed_min_Varying_isi1000)), "Threshold - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi1000))
# table[1] = "Threshold (Fixed-Varying) ISI1000"
# kable(table)

# Threshold - difference between 250 and 1000
#summarize_posterior(threshold_Fixed_min_Varying_isi250, threshold_Fixed_min_Varying_isi1000, "Threshold: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(threshold_Fixed_min_Varying_isi250 - threshold_Fixed_min_Varying_isi1000))
table[1] = "Threshold: 3-way interaction"
kable(table)

# # Drift - difference between fixed and varying ISI 250
# summarize_posterior(drift_Fixed_min_Varying_isi250, rep(0,length(drift_Fixed_min_Varying_isi250)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI250")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250))
# table[1] = "Drift (Fixed-Varying) ISI250"
# kable(table)
# 
# # Drift - difference between fixed and varying ISI 1000
# summarize_posterior(drift_Fixed_min_Varying_isi1000, rep(0,length(drift_Fixed_min_Varying_isi1000)), "Drift - (Fixed:Acc-Speed) - (Varying: Acc-Speed) ISI1000")
# table = test.params(as.data.frame(drift_Fixed_min_Varying_isi1000))
# table[1] = "Drift (Fixed-Varying) ISI1000"
# kable(table)

# Drift - difference between 250 and 1000
#summarize_posterior(drift_Fixed_min_Varying_isi250, drift_Fixed_min_Varying_isi1000, "drift: ISI250 (2-way) - ISI1000 (2-way)")
table = test.params(as.data.frame(drift_Fixed_min_Varying_isi250 - drift_Fixed_min_Varying_isi1000))
table[1] = "Drift: 3-way interaction"
kable(table)


# # Save the figure
# pdf(file="../../../Manuscript/figures/Figure_Exp6_DDM.pdf",height=4,width=8)
# 
# p = cowplot::plot_grid(Exp6.DDM,
#                        nrow = 1)
# p
# dev.off()

```


### Points in 2D 

```{r, message=FALSE}


drift.rate<- test.params(conditions_drift)[1:8,]

threshold<- test.params(conditions_threshold)[1:8,]


va <- rbind(drift.rate,threshold) %>% separate(parameter,c('parameter','factor','fixed','isi'),'_')

va$factor = as.factor(va$factor)

# va$parameter<-factor(va$parameter,labels=c('Threshold','Drift Rate'))


# data = subset(va,fixed=="Varying")
# data = subset(va,isi=="ISI250")

data = va

# data$parameter = c("Drift","Drift","Drift","Drift","Threshold","Threshold","Threshold","Threshold")

# Long to wide
data = pivot_wider(data = data, 
            id_cols = c(factor,fixed,isi), 
            names_from = parameter, 
            values_from = c("Mean","CI_lower","CI_upper"))

# data$factor = c("Speed", "Accuracy","Speed", "Accuracy")

data$factor = factor(data$factor, levels = c("Speed", "Accuracy"))
levels(data$factor) = c("Speed", "Accuracy")
data$isi = factor(data$isi, levels = c("ISI250", "ISI1000"))

levels(data$isi) = c("ISI250", "ISI1000")

# data$factor = c("Speed", "Accuracy","Speed & Accuracy" )

p<-ggplot(data,aes(x=Mean_Drift, y=Mean_Threshold,colour = factor,shape=fixed)) +
  geom_point(size=5) +
  geom_errorbar(width=0, linewidth=1.1, position=position_dodge(width = .6),aes(xmin=CI_lower_Drift,xmax=CI_upper_Drift,linetype=fixed)) +
  geom_errorbar(width=0, linewidth=1.1, position=position_dodge(width = .6),aes(ymin=CI_lower_Threshold,ymax=CI_upper_Threshold,linetype=fixed))+
  facet_wrap(~isi)+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  ylab("Threshold") + 
  xlab("Drift Rate") + 
  scale_x_continuous(limits = c(2.3,3.6),breaks = c(2.5,3,3.5))+
  scale_y_continuous(limits = c(0.6,1.2))+
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none")  

p

Fig4.DDM = p

kable(va)

# Average over SOA
averages_by_parameter <- va %>%
  group_by(parameter,factor,fixed) %>%
  summarize(Mean = mean(Mean))
kable(averages_by_parameter)
# Conditions of interest

```



## Stats

### Mini meta-analysis


```{r, message=FALSE}
##### 250ms

# Drift - A-S fixed
Diff_Fix = conditions_drift$Drift_Accuracy_Fixed_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Diff_Fix = as.data.frame(Diff_Fix)
h = (hypothesis(Diff_Fix,"Diff_Fix<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Fixed 250ms Drift")

# Drift - A-S varying
Diff_Var = conditions_drift$Drift_Accuracy_Varying_ISI250 - conditions_drift$Drift_Speed_Varying_ISI250
Diff_Var = as.data.frame(Diff_Var)
h = (hypothesis(Diff_Var,"Diff_Var<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying 250ms Drift")

# Drift - Cost
Diff_250 = Diff_Fix - Diff_Var
colnames(Diff_250) = "Diff_250"
h = (hypothesis(Diff_250,"Diff_250<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying Drift")

# Threshold - A-S fixed
Diff_Fix = conditions_threshold$Threshold_Accuracy_Fixed_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
Diff_Fix = as.data.frame(Diff_Fix)
h = (hypothesis(Diff_Fix,"Diff_Fix<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Fixed 250ms Threshold")

# Threshold - A-S varying
Diff_Var = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Speed_Varying_ISI250
Diff_Var = as.data.frame(Diff_Var)
h = (hypothesis(Diff_Var,"Diff_Var<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying 250ms Threshold")

# Threshold - Cost
Diff_250 = Diff_Fix - Diff_Var
colnames(Diff_250) = "Diff_250"
h = (hypothesis(Diff_250,"Diff_250<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying Threshold")

# Distance
Distance_Fixed_250 = sqrt((conditions_drift$Drift_Accuracy_Fixed_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250)**2 + (conditions_threshold$Threshold_Accuracy_Fixed_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250)**2)
Distance_Varying_250 = sqrt((conditions_drift$Drift_Accuracy_Varying_ISI250 - conditions_drift$Drift_Speed_Varying_ISI250)**2 + (conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Speed_Varying_ISI250)**2)
Distance_Diff_250 = Distance_Fixed_250 - Distance_Varying_250
kable(test.params(as.data.frame(Distance_Diff_250)))

# Normalized distance

# Threshold & Drift overall min & max
a_max = max(rbind(conditions_threshold$Threshold_Accuracy_Fixed_ISI250,
                  conditions_threshold$Threshold_Accuracy_Varying_ISI250,
                  conditions_threshold$Threshold_Accuracy_Fixed_ISI1000,
                  conditions_threshold$Threshold_Accuracy_Varying_ISI1000,
                  conditions_threshold$Threshold_Speed_Fixed_ISI250,
                  conditions_threshold$Threshold_Speed_Varying_ISI250,
                  conditions_threshold$Threshold_Speed_Fixed_ISI1000,
                  conditions_threshold$Threshold_Speed_Varying_ISI1000))

a_min = min(rbind(conditions_threshold$Threshold_Accuracy_Fixed_ISI250,
                  conditions_threshold$Threshold_Accuracy_Varying_ISI250,
                  conditions_threshold$Threshold_Accuracy_Fixed_ISI1000,
                  conditions_threshold$Threshold_Accuracy_Varying_ISI1000,
                  conditions_threshold$Threshold_Speed_Fixed_ISI250,
                  conditions_threshold$Threshold_Speed_Varying_ISI250,
                  conditions_threshold$Threshold_Speed_Fixed_ISI1000,
                  conditions_threshold$Threshold_Speed_Varying_ISI1000))

v_max = max(rbind(conditions_drift$Drift_Accuracy_Fixed_ISI250,
                  conditions_drift$Drift_Accuracy_Varying_ISI250,
                  conditions_drift$Drift_Accuracy_Fixed_ISI1000,
                  conditions_drift$Drift_Accuracy_Varying_ISI1000,
                  conditions_drift$Drift_Speed_Fixed_ISI250,
                  conditions_drift$Drift_Speed_Varying_ISI250,
                  conditions_drift$Drift_Speed_Fixed_ISI1000,
                  conditions_drift$Drift_Speed_Varying_ISI1000))

v_min = min(rbind(conditions_drift$Drift_Accuracy_Fixed_ISI250,
                  conditions_drift$Drift_Accuracy_Varying_ISI250,
                  conditions_drift$Drift_Accuracy_Fixed_ISI1000,
                  conditions_drift$Drift_Accuracy_Varying_ISI1000,
                  conditions_drift$Drift_Speed_Fixed_ISI250,
                  conditions_drift$Drift_Speed_Varying_ISI250,
                  conditions_drift$Drift_Speed_Fixed_ISI1000,
                  conditions_drift$Drift_Speed_Varying_ISI1000))

# Normalization
v_rangeNorm <- function(x){
  (x-v_min)/(v_max-v_min)
}
a_rangeNorm <- function(x){
  (x-a_min)/(a_max-a_min)
}

Distance_Fixed_250 = sqrt((v_rangeNorm(conditions_drift$Drift_Accuracy_Fixed_ISI250) - v_rangeNorm(conditions_drift$Drift_Speed_Fixed_ISI250))**2 + (a_rangeNorm(conditions_threshold$Threshold_Accuracy_Fixed_ISI250) - a_rangeNorm(conditions_threshold$Threshold_Speed_Fixed_ISI250))**2)

Distance_Varying_250 = sqrt((v_rangeNorm(conditions_drift$Drift_Accuracy_Varying_ISI250) - v_rangeNorm(conditions_drift$Drift_Speed_Varying_ISI250))**2 + (a_rangeNorm(conditions_threshold$Threshold_Accuracy_Varying_ISI250) - a_rangeNorm(conditions_threshold$Threshold_Speed_Varying_ISI250))**2)

Distance_Diff_250 = Distance_Fixed_250 - Distance_Varying_250
kable(test.params(as.data.frame(Distance_Diff_250)))


##### 1000ms

# Drift - A-S fixed
Diff_Fix = conditions_drift$Drift_Accuracy_Fixed_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000
Diff_Fix = as.data.frame(Diff_Fix)
h = (hypothesis(Diff_Fix,"Diff_Fix<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Fixed 1000ms Drift")

# Drift - A-S varying
Diff_Var = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Speed_Varying_ISI1000
Diff_Var = as.data.frame(Diff_Var)
h = (hypothesis(Diff_Var,"Diff_Var<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying 1000ms Drift")

# Drift - Cost
Diff_1000 = Diff_Fix - Diff_Var
colnames(Diff_1000) = "Diff_1000"
h = (hypothesis(Diff_1000,"Diff_1000<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying Drift")

# Threshold - A-S fixed
Diff_Fix = conditions_threshold$Threshold_Accuracy_Fixed_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000
Diff_Fix = as.data.frame(Diff_Fix)
h = (hypothesis(Diff_Fix,"Diff_Fix<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Fixed 1000ms Threshold")

# Threshold - A-S varying
Diff_Var = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Varying_ISI1000
Diff_Var = as.data.frame(Diff_Var)
h = (hypothesis(Diff_Var,"Diff_Var<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying 1000ms Threshold")

# Threshold - Cost
Diff_1000 = Diff_Fix - Diff_Var
colnames(Diff_1000) = "Diff_1000"
h = (hypothesis(Diff_1000,"Diff_1000<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying Threshold")


# Threshold - Cost
Diff = Diff_250 - Diff_1000
colnames(Diff) = "Diff"
h = (hypothesis(Diff,"Diff<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy vs. Speed Varying Threshold")

# Distance
Distance_Fixed_1000 = sqrt((conditions_drift$Drift_Accuracy_Fixed_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000)**2 + (conditions_threshold$Threshold_Accuracy_Fixed_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000)**2)
Distance_Varying_1000 = sqrt((conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Speed_Varying_ISI1000)**2 + (conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Varying_ISI1000)**2)
Distance_Diff_1000 = Distance_Fixed_1000 - Distance_Varying_1000
kable(test.params(as.data.frame(Distance_Diff_1000)))


# Normalized distance

Distance_Fixed_1000 = sqrt((v_rangeNorm(conditions_drift$Drift_Accuracy_Fixed_ISI1000) - v_rangeNorm(conditions_drift$Drift_Speed_Fixed_ISI1000))**2 + (a_rangeNorm(conditions_threshold$Threshold_Accuracy_Fixed_ISI1000) - a_rangeNorm(conditions_threshold$Threshold_Speed_Fixed_ISI1000))**2)

Distance_Varying_1000 = sqrt((v_rangeNorm(conditions_drift$Drift_Accuracy_Varying_ISI1000) - v_rangeNorm(conditions_drift$Drift_Speed_Varying_ISI1000))**2 + (a_rangeNorm(conditions_threshold$Threshold_Accuracy_Varying_ISI1000) - a_rangeNorm(conditions_threshold$Threshold_Speed_Varying_ISI1000))**2)

Distance_Diff_1000 = Distance_Fixed_1000 - Distance_Varying_1000
kable(test.params(as.data.frame(Distance_Diff_1000)))

```


### Speed (drift) ISI=250


```{r, message=FALSE}

Speed_Goal = conditions_drift$Drift_Speed_Varying_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_V_250 = p


```

### Speed (drift) ISI=1000


```{r, message=FALSE}

Speed_Goal = conditions_drift$Drift_Speed_Varying_ISI1000 - conditions_drift$Drift_Speed_Fixed_ISI1000
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_V_1000 = p


```

### Speed (threshold) ISI=250


```{r, message=FALSE}

Speed_Goal = conditions_threshold$Threshold_Speed_Varying_ISI250 - conditions_threshold$Threshold_Speed_Fixed_ISI250
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_A_250 = p


```

### Speed (threshold) ISI=1000


```{r, message=FALSE}

Speed_Goal = conditions_threshold$Threshold_Speed_Varying_ISI1000 - conditions_threshold$Threshold_Speed_Fixed_ISI1000
Speed_Goal = as.data.frame(Speed_Goal)
h = (hypothesis(Speed_Goal,"Speed_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Speed 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Speed_Goal,aes(x=Speed_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("S Var - S Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Speed_A_1000 = p


```


### Accuracy (drift) ISI=250


```{r, message=FALSE}

Accuracy_Goal = conditions_drift$Drift_Speed_Varying_ISI250 - conditions_drift$Drift_Speed_Fixed_ISI250
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_V_250 = p


```

### Accuracy (drift) ISI=1000


```{r, message=FALSE}

Accuracy_Goal = conditions_drift$Drift_Accuracy_Varying_ISI1000 - conditions_drift$Drift_Accuracy_Fixed_ISI1000
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal<0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Drift rate difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_V_1000 = p


```

### Accuracy (threshold) ISI=250


```{r, message=FALSE}

Accuracy_Goal = conditions_threshold$Threshold_Accuracy_Varying_ISI250 - conditions_threshold$Threshold_Accuracy_Fixed_ISI250
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 250 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_A_250 = p


```

### Accuracy (threshold) ISI=1000


```{r, message=FALSE}

Accuracy_Goal = conditions_threshold$Threshold_Accuracy_Varying_ISI1000 - conditions_threshold$Threshold_Accuracy_Fixed_ISI1000
Accuracy_Goal = as.data.frame(Accuracy_Goal)
h = (hypothesis(Accuracy_Goal,"Accuracy_Goal>0"))
kable(as.data.frame(h$hypothesis),caption="Accuracy 1000 (varying vs. fixed)")


# Plot
p = ggplot(data=Accuracy_Goal,aes(x=Accuracy_Goal)) + 
  geom_histogram(bins = 30,fill="transparent",color="black") + 
  geom_vline(xintercept=0,linetype="dashed",size=1.3) +
  xlab("Threshold difference") + 
  ylab("Frequency") + 
  ggtitle("A Var - A Fix [250]") + 
  # scale_x_continuous(limits = c(-0.7,0.7))+
  # scale_y_continuous(limits = c(0,2600),expand = c(0,0))+
  theme(axis.line = element_line(colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = c(0.30, 0.85),
        legend.background = element_rect(fill = "transparent", color = NA)) 

p


Fig4.DDM_Diff_Accuracy_A_1000 = p


```













# Simulations



## Import the data

### Import

```{r, message=FALSE}
# Import, tidy, and merge the simulations data
sim_data = read.csv("../model_simulations/Experiment6.csv")

# Change condition names
sim_data$condition = ifelse(sim_data$condition==0,"Speed","Accuracy")

# Change variable names
colnames(sim_data) = c("soa","factor","fixed","Mean_Drift","Mean_Threshold","v_star","a_star")

# Order the factor
sim_data$factor = factor(sim_data$factor,levels = c("Speed", "Accuracy"))


```

### Summary table

```{r, message=FALSE}


kable(sim_data)

```

## Plot


```{r, message=FALSE}

p<-ggplot(sim_data,aes(x=Mean_Drift, y=Mean_Threshold,colour = factor,shape=fixed)) +
  geom_point(size=5) +
  facet_wrap(~soa)+
  scale_color_viridis(discrete = TRUE ,option = "plasma",end=0.7)+
  ylab("Threshold") + 
  xlab("Drift Rate") + 
  scale_x_continuous(limits = c(2.3,3.6),breaks = c(2.5,3,3.5))+
  scale_y_continuous(limits = c(0.6,1.2))+
  theme(axis.line = element_line(colour = "black"),
        plot.margin=grid::unit(c(5,5,5,5), "mm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0),color="black"),
        text = element_text(size=33,color = "black"),
        panel.border = element_rect (colour = "black", fill = F),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        axis.ticks = element_line(color = "black"),
        legend.position = "none")  

p

Fig4.DDM_sim = p



```



# Save the figures


```{r, message=FALSE}

# Save the figure
pdf(file="../../../Manuscript/figures/Figure_4_DDM&Sim.pdf",height=6,width=15.5)

p = cowplot::plot_grid(Fig4.DDM_sim,
                       Fig4.DDM,
                       nrow = 1,
                       ncol = 2)
p
dev.off()

```

